### 2024-02-10 paper.qmd
first commit

---
title: "Market Expectations and Mangerial Turnover"
author: 
  - Ronan Gallagher
  - Barry Quinn
format: 
    pdf:
      fig-pos: "H"
bibliography: references.bib
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
#| include: false
rm(list = ls())
library(brms)
library(tidyverse)
library(rstan)
library (tidybayes)

logit_baseline<-readRDS("./model/logit_poach_base.rds")
hazard_cty<-readRDS("./model/grp_lvl_poach_cty.rds")
hazard_season<-readRDS("./model/grp_lvl_poach_season.rds")
hazard_div <- readRDS("./model/grp_lvl_poach_div.rds")
logit_cty <-readRDS("./model/logit_grp_lvl_poach_cty.rds")
logit_div <- readRDS("./model/logit_grp_lvl_poach_div.rds")
logit_season <- readRDS("./model/logit_grp_lvl_poach_season.rds")

hazard_div |>   
  spread_draws(r_Div[Division,Variable]) |>
  pivot_wider(names_from = Variable,values_from = r_Div) |>
  left_join(hazard_div 
            |> spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),
            by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won +
           Intercept+Pct_of_Possible_Points_Won) -> hazard_div

logit_div |>   
  spread_draws(r_Div[Division,Variable]) |>
  pivot_wider(names_from = Variable,values_from = r_Div) |>
  left_join(logit_div |> 
              spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),
            by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won+
           Intercept+Pct_of_Possible_Points_Won) -> logit_div

hazard_cty |>
  spread_draws(r_country[Country,Variable]) |>
  pivot_wider(names_from = Variable,values_from = r_country) |>
  left_join(hazard_cty |> spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),
            by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won+
           Intercept+Pct_of_Possible_Points_Won) -> hazard_cty

logit_cty |>
  spread_draws(r_country[Country,Variable]) |>
  pivot_wider(names_from = Variable,values_from =r_country) |>
  left_join(logit_cty |> spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),
            by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won+
           Intercept+Pct_of_Possible_Points_Won) -> logit_cty

hazard_season |>
  spread_draws(r_Season[Season,Variable]) |>
  pivot_wider(names_from = Variable,values_from = r_Season) |>
  left_join(hazard_season |> spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),
            by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won+
           Intercept+Pct_of_Possible_Points_Won) -> hazard_season

logit_season |>
  spread_draws(r_Season[Season,Variable]) |>
  pivot_wider(names_from = Variable,values_from = r_Season) |>
  left_join(logit_season |> spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won),by=c(".chain",'.iteration')) |>
  mutate(conditional_mean_CumRS=b_Standardized_CumRS+Intercept+Standardized_CumRS,
         conditional_mean_Pcts_of_Possible=b_Pct_of_Possible_Points_Won+Intercept+Pct_of_Possible_Points_Won) -> logit_season

```

```{r}
# Creating the named vector in R
cty_factor_vector <- c('E' = "England", 'SP' = "Spain", 'SC' = "Scotland", 'I' = "Italy",
                    'F' = "France", 'D' = "Germany", 'P' = "Portugal", 
                    'N' = "Netherlands", 'T' = "Turkey", 'G' = "Greece", 
                    'B' = "Belgium")
# Assuming df$factor_var is your factor variable
logit_cty$cty_factor <- factor(logit_cty$Country, labels = cty_factor_vector)
hazard_cty$cty_factor <- factor(hazard_cty$Country, labels = cty_factor_vector)
```

# Introduction

# Literature

**CEO Turnover and Firm Performance**

A robust body of research demonstrates a negative correlation between poor organizational performance and involuntary CEO dismissal (@defond1999effect). Both stock returns and accounting metrics indicate that failing to achieve performance benchmarks raises turnover probability, though the magnitude of effects prove statistically significant yet substantively minimal across analyses [@gibbons1990relative; @farrell2003impact].

Building on seminal insights by @march1958organizations and @cyert1963behavioral, subsequent scholarship illuminates how boards of directors explore solutions and prompt managerial changes when results underperform expectations. Managers able to realise forecasted outputs appear less susceptible to replacement than those unable to reach projected thresholds, irrespective of analogous absolute performance [@bandura1991self; @haleblian2006cognitive]. Boards frequently assess leaders against firm-specific expectations, benchmarking actual versus anticipated outcomes and attributing divergence to the CEO [@greve1998performance; @defond1999effect; @wiersema2011ceo]. As proxies for performance expectations, earnings forecasts strongly predict turnover likelihood, though also capture managerial efforts toward systematic issue management [@ieper2014performance]

**Strategic Expectations Management**

Endogeneity concerns thus emerge, as information asymmetries afford CEOs latitude to strategically time media announcements and influence external stakeholder interpretations [@westphal2010matter; @westphal2011avoiding]. Similarly, football managers degrade expectations through injury pronouncements and other excuses that deflect responsibility. Evidence remains limited regarding precise managerial tactics shaping performance benchmarks [@pieper2014performance]. Some research proposes that higher expectations decrease capital costs and increase share prices [@francis1997relative], while other studies indicate systematic “expectation management” wherein CEOs restrict forecast escalation [@bartov2002rewards; @goyal2002board]. This restraint purportedly reduces involuntary turnover incidence.

The majority of empirical literature upholds poor performance as the primary antecedent of managerial replacement [@groves1995china; @hudson2004managerial]. Though post-succession improvements appear frequently observed, findings regarding causal impacts on organizational outcomes remain mixed [@cools2003value]. Difficulties persist in identifying relevant temporal lags and indicators within corporate performance-turnover analyses.

**Parallels in Sport**

In drawing parallels with corporate leadership, football managers constitute integral strategic and operational decision-makers whose choices shape competitiveness and results [@pieper2014performance]. While factors like injuries constrain agency, negative performance often escalates dismissal odds given close linkages between the managerial role and team outputs [@hoffler2003new]. Contemporary scholarship utilizing bookmaker odds reveals that failure to achieve expected sporting outcomes precipitates coaching turnover [@pieper2014performance; @vanours2016inseason; @bruinshoofd2003manager].

In a rare longitudinal approach, @bachan2005hazard model seasonal hazard rates, determining league position overrides individual attributes in predicting managerial survival. Yet other analyses of match outcomes bypass control group issues while accounting for difficulty variances. @koning2003econometric and @forrest2000behaviour find sporadic evidence that replacement temporarily boosts performance. But several studies propose frequent “scapegoating” wherein termination aims to appease stakeholders rather than improve competition, with managerial change reliably hampering short-term results [@koning2003econometric; @dobson2011economics; @audas2002impact].

@tena2007within importantly highlight financial relegation risks and failing historical powers as motivational factors. While the former escalates turnover incidence, the latter proves insignificant as inferior clubs primarily dismissed coaches. Ultimately, teams appear to utilize termination following perceived underperformance relative to expectations shaped by factors like salary budgets.

# Methodology

A primary objective when modeling panel data grouped by country, sports leagues, seasons or other categories is allowing for and assessing systematic differences in effects across groups. Standard panel data techniques like fixed effects or random effects models enable some degree of heterogeneity by permitting intercept variation across groups @greene2003econometric. However, these approaches constrain slope coefficients and error variances to be constant. This could overlook meaningful group-level distributions in parameters beyond intercepts.

Hierarchical Bayesian (HB) models instead provide a cohesive framework for directly specifying group-level distributions for any parameters that may logically vary across categories @gelman2013bayesian. Hierarchical Bayesian (HB) models allow both individual and group-level estimates through partial pooling across the model hierarchy. The group-level distributions essentially serve as priors that regularize or shrink the extreme individual-level parameter estimates towards the group mean. At the same time, the group-level estimates themselves are still informed by and capture the cohort and contextual influences from the individual data.

So partial pooling provides a balanced trade-off - it shrinks less stable individual estimates to avoid overfitting, while still allowing the group distributions to represent meaningful variation across cohorts, contexts or other structures in the data. The key idea is that partial pooling up the hierarchy uses the group-level distributions to stabilize and strengthen estimates, while retaining the ability to capture subgroup patterns.

Moreover, HB models facilitate incorporating complex covariance patterns and nonlinear relationships in parameters across groups. @zhang2021racial uses Bayesian cross-classified multilevel analysis to model subtle temporal and group-level interactions in voter turnout - difficult to formulate through panel data methods.

In summary, HB techniques yield a unified modeling approach to characterize inter-group parameter variation. The methodology subsumes traditional panel data econometrics through its flexibility while addressing limitations. The formal probability structure also regulates instability and provides natural group-level effect quantification - particularly critical when data within clusters is sparse. This establishes hierarchical Bayesian modeling as a powerful tool for econometric grouped data analyses.

## Model Specification

The models are:

1.  **HB Logit Model**

$$P(\text{Poached}_{i} = 1 | \text{Points}_{i}, \text{RSI}_{i}) = \mathrm{logit}^{-1}(\alpha_{l[i]} + \beta_{1,l[i]} \text{Points}_{i} + \beta_{2,l[i]} \text{RSI}_{i} + \epsilon_{i})$$

2.  **HB Proportional Hazard Model**

$$h(t|X_{i}) = h_{0}(t)\exp(\alpha_{l[i]} + \beta_{1,l[i]} \text{Points}_{i} + \beta_{2,l[i]} \text{RSI}_{i}) $$

The subscript $l[i]$ allows coefficient variation across groups. We investigate hierarchies across season, country and country-tier. Hierarchical priors on $\alpha,\beta$ parameters share data to obtain better estimates, even for new leagues or clubs.

# Results

## Baseline logit model

```{r}
#| label: baseline-logit
#| eval: false
dfanal=read_csv("./data/df_anal_new.csv")
rstan_options(auto_write=TRUE)  
options(mc.cores=parallel::detectCores ()) # Run on multiple cores
#set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
dfanal |> drop_na(event,Standardized_CumRS,Pct_of_Possible_Points_Won,Div,`Domestic Games in Charge`)
dfanal$games_to_event<-dfanal$`Domestic Games in Charge`
model <- brm(poach ~ 1 + Standardized_CumRS + Pct_of_Possible_Points_Won,
             data = dfanal,
             family = bernoulli(), # Specifies a logit model for binary outcome
             warmup = 1000, # Number of warmup iterations for the MCMC
             iter = 5000, # Total number of iterations for the MCMC
             chains = 4, # Number of chains
             cores = 4, # Number of cores for parallel execution
             control = list(adapt_delta = 0.95), # Control parameters for the NUTS sampler
             seed=5678)

end=Sys.time()
print(end-start)
model |> summary()

saveRDS(model ,"logit_poach_base.rds")

```

## Baseline hazard model

## group level logit models

```{r}
logit_cty |> 
  ungroup() |>
  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
  group_by(cty_factor,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(cty_factor,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effect on probability of poaching",
       subtitle="Posterior probability distribution",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)

```

```{r}
logit_season |> 
  ungroup() |>
  select(Season,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!Season&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>
  mutate(first_year = as.numeric(map_chr(str_split(Season, "-"), ~ .x[1]))) |>
  ggplot(aes(x = reorder(Season,first_year),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effects on the probability of poaching",
       subtitle="Posterior probabilities from a bayesian hierarchical model",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_by_season.png",width = 12,height = 8)  
```

```{r}
logit_div |> 
  ungroup() |>
  select(Division,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!Division &!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |> 
   group_by(Division,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(Division,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effects on the probability of poaching",
       subtitle="Posterior probabilities from a bayesian hierarchical model",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/logit_by_div.png",width = 12,height = 8)  
```

## group level hazard models

```{r}
hazard_cty |> 
  ungroup() |>
  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
  group_by(cty_factor,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(cty_factor,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effect on poaching hazard rate",
       subtitle="Posterior probability distribution",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/hazard_by_cty.png",width = 12,height = 8)

```

```{r}
hazard_season |> 
  ungroup() |>
  select(Season,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!Season&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>
  mutate(first_year = as.numeric(map_chr(str_split(Season, "-"), ~ .x[1]))) |>
  ggplot(aes(x = reorder(Season,first_year),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effects on the probability of poaching",
       subtitle="Posterior probabilities from a bayesian hierarchical model",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/hazard_by_season.png",width = 12,height = 8)  
```

```{r}
hazard_div |> 
  ungroup() |>
  select(Division,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
  pivot_longer(!Division&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
  group_by(Division,conditional_mean) |>
  mutate(global_mean=mean(draws)) |>
  ggplot(aes(x = reorder(Division,global_mean),
             y=draws, 
             fill =conditional_mean)) +
  stat_slab() +
  labs(x="",
       title="Overall effect on poaching hazard rate",
       subtitle="Posterior probability distribution",
       y="Overall Effect",fill="")  +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        title = element_text(hjust = 0.5),
        legend.position = "bottom") +
  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
ggsave(filename = "./plots/hazard_by_div.png",width = 12,height = 8)

```

### 2024-02-10 paper.qmd
updated repo

@@
 
-logit_baseline<-readRDS("./model/logit_poach_base.rds")
-hazard_cty<-readRDS("./model/grp_lvl_poach_cty.rds")
-hazard_season<-readRDS("./model/grp_lvl_poach_season.rds")
-hazard_div <- readRDS("./model/grp_lvl_poach_div.rds")
-logit_cty <-readRDS("./model/logit_grp_lvl_poach_cty.rds")
-logit_div <- readRDS("./model/logit_grp_lvl_poach_div.rds")
-logit_season <- readRDS("./model/logit_grp_lvl_poach_season.rds")
+logit_baseline<-readRDS("models/logit_poach_base.rds")
+hazard_cty<-readRDS("models/grp_lvl_poach_cty.rds")
+hazard_season<-readRDS("models/grp_lvl_poach_season.rds")
+hazard_div <- readRDS("models/grp_lvl_poach_div.rds")
+logit_cty <-readRDS("models/logit_grp_lvl_poach_cty.rds")
+logit_div <- readRDS("models/logit_grp_lvl_poach_div.rds")
+logit_season <- readRDS("models/logit_grp_lvl_poach_season.rds")
 

### 2024-02-10 bayesian_estimation.R

@@ -1,0 +1,155 @@
+rm(list=ls())
+library(brms)
+library(tidyverse)
+library(rstan)
+library(cmdstanr)
+library(survival)
+library (coda)
+library (bayesplot)
+library (shinystan)
+library (tidybayes)
+
+## recommended by tidybayes vignette
+library (magrittr)
+library (dplyr)
+library (purrr)
+library (forcats)
+library (tidyr)
+library (modelr)
+library (ggplot2)
+library (ggstance)
+library (cowplot)
+library (rstan)
+library (ggrepel)
+library (RColorBrewer)
+library (gganimate)
+
+theme_set(theme_tidybayes() + panel_border())
+
+read_csv("./data/df_anal.csv")->dfanal
+
+rstan_options(auto_write=TRUE)
+options(mc.cores=parallel::detectCores ()) # Run on multiple cores
+set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
+dfanal |> drop_na(event,Standardized_CumRS,Pct_of_Possible_Points_Won,Div,`Domestic Games in Charge`)
+table(dfanal$country)
+  
+
+dfanal$games_to_event<-dfanal$`Domestic Games in Charge`
+Sys.time ()
+mgrs.indiv.brm.test <- brm ((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS
+                            + Pct_of_Possible_Points_Won +                                                                                                                
+                              (1 | Div ) + (-1 + Pct_of_Possible_Points_Won|Div) + (-1 +  Standardized_CumRS|Div),
+                            dfanal, family= weibull (),backend = "cmdstan", warmup= 5, iter= 10, seed= 5781)
+Sys.time()
+mgrs.indiv.brm <- brm ((games_to_event) | cens (poach) ~ - 1 + Standardized_CumRS
+                            + Pct_of_Possible_Points_Won +
+                              (1 | country ) + (-1 + Pct_of_Possible_Points_Won|country) + 
+                         (-1 +  Standardized_CumRS|country),
+                            dfanal, family= weibull (), warmup= 500,iter = 2000, seed= 5781)
+Sys.time()
+
+Sys.time()
+mgrs.indiv.brm.sack.div <- brm ((games_to_event) | cens (sack) ~ - 1 + 
[…]

### 2024-02-10 bayesian_estimation.R
update

@@ -2,154 +2,22 @@ rm(list=ls())
 library(brms)
 library(tidyverse)
 library(rstan)
-library(cmdstanr)
 library(survival)
-library (coda)
-library (bayesplot)
-library (shinystan)
 library (tidybayes)
-
-## recommended by tidybayes vignette
-library (magrittr)
-library (dplyr)
-library (purrr)
-library (forcats)
-library (tidyr)
-library (modelr)
-library (ggplot2)
-library (ggstance)
-library (cowplot)
-library (rstan)
-library (ggrepel)
-library (RColorBrewer)
-library (gganimate)
-
-theme_set(theme_tidybayes() + panel_border())
-
-read_csv("./data/df_anal.csv")->dfanal
-
+library(readr)
+read_csv("dat_part1.csv") |>
+  bind_rows(read_csv("dat_part2.csv")) -> dfanal
 rstan_options(auto_write=TRUE)
 options(mc.cores=parallel::detectCores ()) # Run on multiple cores
-set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
+#set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
 dfanal |> drop_na(event,Standardized_CumRS,Pct_of_Possible_Points_Won,Div,`Domestic Games in Charge`)
-table(dfanal$country)
-  
-
 dfanal$games_to_event<-dfanal$`Domestic Games in Charge`
-Sys.time ()
-mgrs.indiv.brm.test <- brm ((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS
-                            + Pct_of_Possible_Points_Won +                                                                                                                
-                              (1 | Div ) + (-1 + Pct_of_Possible_Points_Won|Div) + (-1 +  Standardized_CumRS|Div),
-                            dfanal, family= weibull (),backend = "cmdstan", warmup= 5, iter= 10, seed= 5781)
-Sys.time()
-mgrs.indiv.brm <- brm ((games_to_event) | cens (poach) ~ - 1 + Standardized_CumRS
-                            + Pct_of_Possible_Points_Won +
-                              (1 | country ) + (-1 + Pct_of_Possible_Points_Won|country) + 
-                         (-1 +  Standardized_CumRS|country),
[…]

### 2024-02-23 paper.qmd
tidy up and more detail

@@
 logit_season <- readRDS("models/logit_grp_lvl_poach_season.rds")
+
+logit_baseline |> 
+  spread_draws(b_Standardized_CumRS,b_Pct_of_Possible_Points_Won)->logit_baseline
 
@@
 
+# Data
+
 # Methodology
@@
 #| eval: false
+# This code is set yo not run, to set to run change eval to eval: true
 dfanal=read_csv("./data/df_anal_new.csv")
@@
 saveRDS(model ,"logit_poach_base.rds")
+
+```
+
+```{r}
+logit_baseline |>
+  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
+         "Cumulative Relative Strength"=b_Standardized_CumRS)
+  pivot_longer(!.draw&!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
+  ggplot(aes(y = fixed_effect,
+             x=draws)) +
+  stat_slab() +
+  labs(x="",
+       title="Baseline model for probability of poaching",
+       subtitle="Posterior probability distribution",
+       y="Fixed Effect",fill="")  +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        title = element_text(hjust = 0.5),
+        legend.position = "bottom") +
+  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
+ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
 

### 2024-02-23 paper.qmd
some local changes in linux machine

--- 2024-02-10 paper.qmd
@@
 
+The $t$ is the time to hazard in games in charges.
 The subscript $l[i]$ allows coefficient variation across groups.
@@
 saveRDS(model ,"logit_poach_base.rds")
+
+```
+
+```{r}
+logit |> 
+  ungroup() |>
+  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
+  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
+  group_by(cty_factor,conditional_mean) |>
+  mutate(global_mean=mean(draws)) |>
+  ggplot(aes(x = reorder(cty_factor,global_mean),
+             y=draws, 
+             fill =conditional_mean)) +
+  stat_slab() +
+  labs(x="",
+       title="Overall effect on probability of poaching",
+       subtitle="Posterior probability distribution",
+       y="Overall Effect",fill="")  +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        title = element_text(hjust = 0.5),
+        legend.position = "bottom") +
+  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
+ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)
 

### 2024-02-23 paper.qmd

--- 2024-02-23 paper.qmd
@@
 ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
+
+```
+
+```{r}
+logit_baseline |>
+  rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
+         "Cumulative Relative Strength"=b_Standardized_CumRS)
+  pivot_longer(!.draw&!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
+  ggplot(aes(y = fixed_effect,
+             x=draws)) +
+  stat_slab() +
+  labs(x="",
+       title="Baseline model for probability of poaching",
+       subtitle="Posterior probability distribution",
+       y="Fixed Effect",fill="")  +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        title = element_text(hjust = 0.5),
+        legend.position = "bottom") +
+  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
+ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
+
+```
+
+```{r}
+logit |> 
+  ungroup() |>
+  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
+  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
+  group_by(cty_factor,conditional_mean) |>
+  mutate(global_mean=mean(draws)) |>
+  ggplot(aes(x = reorder(cty_factor,global_mean),
+             y=draws, 
+             fill =conditional_mean)) +
+  stat_slab() +
+  labs(x="",
+       title="Overall effect on probability of poaching",
+       subtitle="Posterior probability distribution",
+       y="Overall Effect",fill="")  +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        title = element_text(hjust = 0.5),
+        legend.position = "bottom") +
+  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
+ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)
 

### 2024-02-23 paper.qmd
sdfdsf

@@
 library (tidybayes)
+reticulate::use_condaenv("pymc")
 
@@
 # Data
+
+## Manager spell profiles
+We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024.  We use 
+three sources 1.
+[league of managers association](https://leaguemanagers.com) a body representing professional managers in English football.
+2.
+[Soccer base](https://www.soccerbase.com) a betting website 3.
+[Transfermkt website](https://www.transfermarkt.co.uk) a large website which records manager, player and team profiles as well as a large array of analytics of the valuation of playing staff.
+The raw data is gathered using a series of web scrapping algorithms.
+Our primary source of informatoin is Transfermkt, but we use other sources to validate these manager spells.
+
+```{python}
+import pandas as pd
+from pandas_profiling import ProfileReport
+
+spells_raw = pd.read_csv("raw_data/club_manager_histories_df.csv")
+
+# Generating a report
+profile = ProfileReport(spells_raw, title="Profile data", explorative=True)
+
+# To display the report within a Jupyter Notebook
+profile.to_notebook_iframe()
+```
 

### 2024-02-23 bayesian_estimation.R

@@ -1,23 +1,0 @@
-rm(list=ls())
-library(brms)
-library(tidyverse)
-library(rstan)
-library(survival)
-library (tidybayes)
-library(readr)
-read_csv("dat_part1.csv") |>
-  bind_rows(read_csv("dat_part2.csv")) -> dfanal
-rstan_options(auto_write=TRUE)
-options(mc.cores=parallel::detectCores ()) # Run on multiple cores
-#set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
-dfanal |> drop_na(event,Standardized_CumRS,Pct_of_Possible_Points_Won,Div,`Domestic Games in Charge`)
-dfanal$games_to_event<-dfanal$`Domestic Games in Charge`
-# Sys.time ()
-# mgrs.indiv.brm.test <- brm ((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS
-#                             + Pct_of_Possible_Points_Won +                                                                                                                
-#                               (1 | Div ) + (-1 + Pct_of_Possible_Points_Won|Div) + (-1 +  Standardized_CumRS|Div),
-#                             dfanal, family= weibull (),backend = "cmdstan", warmup= 5, iter= 10, seed= 5781)
-# Sys.time()
-
-model <- brm((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS + Pct_of_Possible_Points_Won
-             ,warmup = 1000,iter = 5000,data = dfanal)

### 2024-02-23 bayesian_estimation.py

@@ -1,32 +1,0 @@
-import pandas as pd
-import pymc as pm
-import numpy as np
-import arviz as az
-
-# Load data
-df1 = pd.read_csv('dat_part1.csv')
-df2 = pd.read_csv('dat_part1.csv')
-data = pd.concat([df1, df2], ignore_index=True)
-
-# Outcome and predictors 
-y = data['poach'] 
-X = data[["Standardized_CumRS", "Pct_of_Possible_Points_Won"]]
-
-# Logistic model 
-with pm.Model() as model:
-    alpha = pm.Normal('alpha', mu=0, sd=10)
-    beta = pm.Normal('beta', mu=0, sd=1, shape=2)  
-    
-    p = pm.invlogit(alpha + beta[0]*X["Standardized_CumRS"] + beta[1]*X["Pct_of_Possible_Points_Won"])
-    
-    outcome = pm.Bernoulli('outcome', p=p, observed=y)
-    
-    trace = pm.sample(2000, chains=2)
-    
-# Save trace 
-az.to_netcdf(trace, 'logreg_trace.nc')
-
-# Check trace 
-az.summary(trace)
-
-

### 2024-02-23 scripts/bayesian_estimation.R

@@ -1,0 +1,23 @@
+rm(list=ls())
+library(brms)
+library(tidyverse)
+library(rstan)
+library(survival)
+library (tidybayes)
+library(readr)
+read_csv("dat_part1.csv") |>
+  bind_rows(read_csv("dat_part2.csv")) -> dfanal
+rstan_options(auto_write=TRUE)
+options(mc.cores=parallel::detectCores ()) # Run on multiple cores
+#set_cmdstan_path(path="/home/barry/.cmdstan/cmdstan-2.33.1")
+dfanal |> drop_na(event,Standardized_CumRS,Pct_of_Possible_Points_Won,Div,`Domestic Games in Charge`)
+dfanal$games_to_event<-dfanal$`Domestic Games in Charge`
+# Sys.time ()
+# mgrs.indiv.brm.test <- brm ((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS
+#                             + Pct_of_Possible_Points_Won +                                                                                                                
+#                               (1 | Div ) + (-1 + Pct_of_Possible_Points_Won|Div) + (-1 +  Standardized_CumRS|Div),
+#                             dfanal, family= weibull (),backend = "cmdstan", warmup= 5, iter= 10, seed= 5781)
+# Sys.time()
+
+model <- brm((games_to_event) | cens (poach) ~ 1 + Standardized_CumRS + Pct_of_Possible_Points_Won
+             ,warmup = 1000,iter = 5000,data = dfanal)

### 2024-02-23 scripts/bayesian_estimation.py

@@ -1,0 +1,32 @@
+import pandas as pd
+import pymc as pm
+import numpy as np
+import arviz as az
+
+# Load data
+df1 = pd.read_csv('dat_part1.csv')
+df2 = pd.read_csv('dat_part1.csv')
+data = pd.concat([df1, df2], ignore_index=True)
+
+# Outcome and predictors 
+y = data['poach'] 
+X = data[["Standardized_CumRS", "Pct_of_Possible_Points_Won"]]
+
+# Logistic model 
+with pm.Model() as model:
+    alpha = pm.Normal('alpha', mu=0, sd=10)
+    beta = pm.Normal('beta', mu=0, sd=1, shape=2)  
+    
+    p = pm.invlogit(alpha + beta[0]*X["Standardized_CumRS"] + beta[1]*X["Pct_of_Possible_Points_Won"])
+    
+    outcome = pm.Bernoulli('outcome', p=p, observed=y)
+    
+    trace = pm.sample(2000, chains=2)
+    
+# Save trace 
+az.to_netcdf(trace, 'logreg_trace.nc')
+
+# Check trace 
+az.summary(trace)
+
+

### 2024-02-23 scripts/data_prep.py

@@ -1,0 +1,46 @@
+import pandas as pd
+df_anal=pd.read_csv("./data/df_anal.csv")
+df_anal['event'] = df_anal['event'].astype('category')
+df_anal['event'] = df_anal['event'].cat.reorder_categories(['Still in the job', 'A sacking', 'A poaching'])
+df_anal['event_code'] = df_anal['event'].cat.codes  # Create a new column for the codes
+df_anal=df_anal[df_anal['event_code']!=-1]
+Duration=df_anal['Domestic Games in Charge']#predictors = ['Standardized_CumRS','Pct_of_Possible_Points_Won']
+event=df_anal['event_code']
+dummies = pd.get_dummies(df_anal['event'],prefix='event')
+df_anal = pd.concat([df_anal,dummies] , axis=1)
+# Extract and recategories the country codes to names
+df_anal['Div_letter'] = df_anal['Div'].str.extract(r'([a-zA-Z]+)').apply(lambda x: ''.join(x), axis=1)
+df_anal['Div_letter'] = df_anal['Div_letter'].astype('category')
+df_anal['Div_letter'].value_counts()
+dict = {'E': 'England', 'SP': 'Spain', 'SC':'Scotland','I': 'Italy', 'F': 'France', 'D': 'Germany', 'P': 'Portugal', 'N': 'Netherlands', 'T': 'Turkey', 'G': 'Greece', 'B': 'Belgium', 'G': 'Greece'}
+df_anal['Country'] = df_anal['Div_letter'].map(dict)
+df_anal['Country'] = df_anal['Country'].astype('category')
+df_anal['Tier']=df_anal['Div'].str.extract(r'(\d+)')
+df_anal=df_anal[(df_anal['Domestic Games in Charge']>5) & (df_anal['days_btw_spells']>=0)]
+# Find the last game of each season
+df_anal['Date'] = pd.to_datetime(df_anal['Date'])
+Season_Ends = df_anal.drop_duplicates(['Div', 'Date'])
+# Calculate how many days were between the last game of the season and the first game of the next season
+Season_Ends['days_between_games'] = (Season_Ends['Date'] - Season_Ends.groupby(['Div'])['Date'].shift()).dt.days
+# Keep only the last game of the season if it was at least 60 days away from the first game of the next season
+Season_Ends = Season_Ends[Season_Ends['days_between_games'] > 60]
[…]

### 2024-02-23 scripts/data_prep_master_new.R

@@ -1,0 +1,220 @@
+#### load data and software ####
+DeleteList<-ls()
+rm(list=DeleteList)
+pacman::p_load(tidyverse,implied,lubridate,pracma,googledrive,plotly,install = F)
+tf_records<-readRDS("data/transfermkt_managers_new.rds")
+match_dat<-readRDS("data/matches_raw.rds") %>%
+  mutate(Date=dmy(Date)) %>% 
+  drop_na(Date)
+index<-readRDS("data/master_name_match_df.rds")
+index %>% 
+  filter(duplicated(tm_name)|
+           duplicated(tm_name,fromLast=T)|
+           duplicated(fd_name)|
+           duplicated(fd_name,fromLast=T)) -> duplicates
+# preprocess  ---
+# filtering the raw transfermkt records
+tf_records %>%
+  filter(position=="Manager") %>% # 1. filter on managers type 
+  filter(Start>=first(match_dat$Date)) %>% # 2. filter to full odds record for spell
+  filter(club %in% index$tm_name) %>% # 3. All clubs in index
+  filter(!club %in% duplicates$tm_name) %>% # 4. remove clubs which are duplicated for tm_name
+  filter(!club %in% duplicates$fd_name) %>% # 4. remove clubs which are duplicated for fd_name
+  arrange(name,Start,Finish) %>%
+  group_by(name) %>%
+  mutate(spell_between_jobs=as.numeric(lead(Start)-Finish)) %>% 
+  ungroup() %>%
+  group_by(club,name) %>%
+  mutate(spell_no_with_club=n()) %>%
+  ungroup() %>%
+  mutate(spell_between_jobs=if_else(spell_between_jobs>=-60 & spell_between_jobs<0,0,
+                                    spell_between_jobs))-> tf_records
+saveRDS(tf_records,"data/tf_records_raw.rds")
+## Season ends per league and division
+  match_dat %>%
+  distinct(league,Div,Date) %>%
+   group_by(league,Div) %>%
+   mutate(days_between_games=as.numeric(Date-lag(Date))) %>%
+   filter(days_between_games>60) %>%
+   mutate(Year=year(Date)) %>%
+   distinct(league,Div,Year,.keep_all = T) %>%
+   rename(Season_Start=Date)-> Season_Ends
+#### Season ####
[…]

### 2024-02-23 scripts/football-data-scrape.R

@@ -1,0 +1,146 @@
+MyDeleteItems<-ls()
+rm(list=MyDeleteItems)
+library(tidyverse)
+library(rio)
+
+# Import data from Seasons 2000-2001 to  2019-2020 from http://www.football-data.co.uk
+
+seasons<-c("0001","0102","0203","0304","0405",
+           "0506","0607","0708","0809","0910",
+           "1011","1112","1213","1314","1415",
+           "1516","1617","1718","1819","1920",
+           "2021","2122","2223")
+
+leagues<-c("England","Scotland","Germany","Italy","Spain","France",
+           "Netherlands","Belgium","Portugal","Turkey","Greece")
+
+euro_matches<-vector("list",length =length(leagues) )
+names(euro_matches)<-leagues
+dlist<-list()
+i=0
+for (s in seasons) {
+  for (l in c("E0","E1","E2","E3")) {
+    i=i+1
+    url<-paste0('https://www.football-data.co.uk/mmz4281/',s,"/",l,".csv")
+    df<-read_csv(url)
+    df %>% map_df(as.character)->df
+    dlist[[i]]<-df
+  }
+}
+euro_matches[['England']]<-bind_rows(dlist)
+
+dlist<-list()
+i=0
+for (s in seasons) {
+  for (l in c("SC0","SC1","SC2","SC3")) {
+    i=i+1
+    url<-paste0('https://www.football-data.co.uk/mmz4281/',s,"/",l,".csv")
+    df<-read_csv(url)
+    df %>% map_df(as.character)->df
+    dlist[[i]]<-df
+  }
+}
+euro_matches[['Scotland']]<-bind_rows(dlist)
+dlist<-list()
+i=0
+for (s in seasons) {
+  for (l in c("D1","D2")) {
+    i=i+1
+    url<-paste0('https://www.football-data.co.uk/mmz4281/',s,"/",l,".csv")
+    df<-read_csv(url)
+    df %>% map_df(as.character)->df
+    dlist[[i]]<-df
+  }
+}
+euro_matches[['Germany']]<-bind_rows(dlist)
+dlist<-list()
+i=0
+for (s in seasons) {
+  for (l in c("I1","I2")) {
+    i=i+1
+    url<-paste0('https://www.football-data.co.uk/mmz4281/',s,"/",l,".csv")
+    df<-read_csv(url)
[…]

### 2024-02-23 scripts/transfer-market-scrape.R

@@ -1,0 +1,228 @@
+rm(list = ls())
+library(worldfootballR)
+library(tidyverse)
+library(progress)
+library(stringr)
+# Create a list of League URLs of Interest ----
+
+#To test the code I run with the top two English tiers. (In reality we want to loop it across an expanded list of the ilk commented below)
+#league_links = list("https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB1", "https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB2")
+#Here I have the top 4 tiers in England and the top two in Spain, Germany, France, Italy, Holland, Belgium, Portugal, Turkey, Greece and Scotland
+league_links = c("https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB1", 
+                    "https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB2", 
+                    "https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB3", 
+                    "https://www.transfermarkt.com/league-one/startseite/wettbewerb/GB4", 
+                    "https://www.transfermarkt.com/primera-division/startseite/wettbewerb/ES1", 
+                    "https://www.transfermarkt.com/primera-division/startseite/wettbewerb/ES2", 
+                    "https://www.transfermarkt.com/bundesliga/startseite/wettbewerb/L1", 
+                    "https://www.transfermarkt.com/bundesliga/startseite/wettbewerb/L2", 
+                    "https://www.transfermarkt.com/ligue-1/startseite/wettbewerb/FR1", 
+                    "https://www.transfermarkt.com/ligue-1/startseite/wettbewerb/FR2", 
+                    "https://www.transfermarkt.com/serie-a/startseite/wettbewerb/IT1",
+                    "https://www.transfermarkt.com/serie-a/startseite/wettbewerb/IT2", 
+                    "https://www.transfermarkt.com/super-lig/startseite/wettbewerb/TR1",
+                    "https://www.transfermarkt.com/super-lig/startseite/wettbewerb/TR2", 
+                    "https://www.transfermarkt.com/super-league-1/startseite/wettbewerb/GR1", 
[…]

### 2024-02-23 paper.qmd
some adaptions

@@
 
-```{python}
-import pandas as pd
-from pandas_profiling import ProfileReport
+```{r}
+library(readxl)
+spells_raw = read_csv("raw_data/club_manager_histories_df.csv")
+skimr::skim(spells_raw)
 
-spells_raw = pd.read_csv("raw_data/club_manager_histories_df.csv")
-
-# Generating a report
-profile = ProfileReport(spells_raw, title="Profile data", explorative=True)
-
-# To display the report within a Jupyter Notebook
-profile.to_notebook_iframe()
 ```
@@
          "Cumulative Relative Strength"=b_Standardized_CumRS)
-  pivot_longer(!.draw&!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
+
+          |>
+  pivot_longer(!.draw &!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
   ggplot(aes(y = fixed_effect,

### 2024-02-24 paper.qmd
some paper updates
update:     git add .     git commit -m "update"     git push

@@
 ## Manager spell profiles
-We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024.  We use 
-three sources 1.
+
+We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024.
+We use three sources 1.
 [league of managers association](https://leaguemanagers.com) a body representing professional managers in English football.
@@
 The raw data is gathered using a series of web scrapping algorithms.
-Our primary source of informatoin is Transfermkt, but we use other sources to validate these manager spells.
+Our primary source of information is Transfermkt, but we use other sources to validate these manager spells.
 
@@
 library(readxl)
-spells_raw = read_csv("raw_data/club_manager_histories_df.csv")
+spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
 skimr::skim(spells_raw)
-
 ```

### 2024-02-25 paper.qmd
some EDA in python

@@
 
-```{r}
-library(readxl)
-spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
-skimr::skim(spells_raw)
+```{python}
+# Read the CSV files
+spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+spells2 = pd.read_csv("raw_data/club_manager_histories_df.csv")
+
+# Get a statistical summary of the data
+summary1 = spells1.describe()
+summary2 = spells2.describe()
+
+print(summary1)
+print(summary2)
+```
+
+```{python}
+# Filter rows where the 'Finish' column is NaN
+filtered_spells1 = spells1[spells1['Finish'].isna()]
+
+# Create a frequency table of the 'contract_expiry' column
+frequency_table = filtered_spells1['contract_expiry'].value_counts()
+
+print(frequency_table)
+```
+
+```{python}
+import numpy as np
+def season_to_date(season):
+    if pd.isnull(season) or '/' not in season:
+        return np.nan
+
+    parts = season.split('/')
+    if int(parts[1]) < 80:
+        year = '20' + parts[1]
+    else:
+        year = '19' + parts[1]
+
+    date_str = '01/08/' + year
+    return datetime.strptime(date_str, '%d/%m/%Y')
+
+```
+
+```{python}
+# Apply the function only to rows where 'Date' is NaN
+mask=spells1['Finish'].isna()
+spells1.loc[mask, 'Finish'] = spells1.loc[mask,'contract_expiry'].apply(season_to_date)
+#spells1[spells1['Finish'].isna()].value_counts()
+spells1['Finish'].isna().value_counts()
 ```

### 2024-02-26 hugging_face_teamnames_info.py
a script to use LLMs to predict extra characteristics of a team name

@@ -1,0 +1,45 @@
+from transformers import pipeline
+import pandas as pd
+generator = pipeline("text-generation")
+# Load model directly
+# from transformers import AutoTokenizer, AutoModelForCausalLM
+# 
+# tokenizer = AutoTokenizer.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")
+# model = AutoModelForCausalLM.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")  
+# Use a pipeline as a high-level helper
+#from transformers import pipeline
+#pipe = pipeline("text-generation", model="mistralai/Mixtral-8x7B-Instruct-v0.1")
+# Example array of professional soccer club names
+spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+club_names=spells1['club'].unique()
+# Initialize an empty list to store the results
+results = []
+
+# Iterate over the array of club names
+for club in club_names:
+    # Prepare the prompt for the model
+    prompt = f"Provide information about the soccer club {club}: its country of origin, division level, and whether it is a first team or a youth team."
+    
+    # Generate the response using the model
+    responses=generator(prompt)
+    
+    # Assuming the first (or only) response is what we're interested in
+    response_text = responses[0]
+    
+    # Store the response in our results list
+    results.append({'ClubName': club, 'Information': response_text})
+
+# Convert the results list to a DataFrame
+import pandas as pd
+results_df = pd.DataFrame(results)
+
+# Display the DataFrame to verify the results
+print(results_df)
+
+# Specify the file path for the CSV file
+csv_file_path = 'soccer_clubs_information_hf.csv'
+
+# Save the DataFrame to a CSV file
+results_df.to_csv(csv_file_path, index=False)
+
+print(f"Results have been saved to {csv_file_path}")

### 2024-02-29 paper.qmd
some updates to descriptive statistics

--- 2024-02-24 paper.qmd
@@
 ```{r}
-library(readxl)
-spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
-skimr::skim(spells_raw)
+library(dplyr)
+library(purrr)
+spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+# Define season_to_date() function here
+season_to_date <- function(season) {
+  if (is.na(season) | length(gsub("/", "", season)) == 0) {
+    return(NA_real_)
+  }
+
+  parts <- strsplit(season, "/")[[1]]
+  month <- as.numeric(parts[2])
+   if (month < 8) {
+     year <- paste0("20", substr(parts[1], 1, 2))
+   } else {
+     year <- paste0("19", substr(parts[1], 1, 2))
+   }
+
+  date_str <- paste0("01/08/", year)
+  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
+}
+
+data_helper <- spells1 |>
+  mutate(row_id=row_number()) |>
+  filter(is.na(Finish)&contract_expiry!="-") |>
+  select(contract_expiry, Finish,row_id)
+data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
+spells |>
+  mutate(row_id=row_number()) |>
+  left_join(data_helper, by="row_id") |>
+  mutate(Start = as.Date(Start),
+         Finish = as.Date(Finish)) |>
+  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
+
+```
+
+```{python}
+import pandas as pd
+import time
+from transformers import pipeline
+
+generator = pipeline("text-generation")
+# Load model directly
+# from transformers import AutoTokenizer, AutoModelForCausalLM
+# 
+# tokenizer = AutoTokenizer.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")
+# model = AutoModelForCausalLM.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")  
+# Use a pipeline as a high-level helper
+#from transformers import pipeline
+#pipe = pipeline("text-generation", model="mistralai/Mixtral-8x7B-Instruct-v0.1")
+
+# Load the unique club names from the CSV file
+spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+club_names=spells1['club'].unique()
+
+# Initialize an empty list to store the results
+results = []
+
+# Iterate over the array of club names and add a timer for each iteration
+start_time = time.time()
+for club in club_names:
+    # Prepare the prompt for the model
+    prompt = f"Provide information about the soccer club {club}: its country of origin,  division level, and whether it is a first  team or a youth team."
+
+    # Generate the response using the model
+    start = time.time()
+    responses=generator(prompt)
+
+    # Assuming the first (or only) response is what we're interested in
+    response_text = responses[0]
+
+    # Store the response, elapsed time for this iteration and total elapsed time in our results list
+    results.append({'ClubName': club, 'Information': response_text, 'ElapsedTimePerIteration': time.time() - start, 
+'TotalElapsedTime': time.time() - start_time})
+
+# Convert the results list to a DataFrame
+import pandas as pd
+results_df = pd.DataFrame(results)
+
+# Display the DataFrame to verify the results
+print(results_df)
+
+# Specify the file path for the CSV file
+csv_file_path = 'soccer_clubs_information_hf.csv'
+
+# Save the DataFrame to a CSV file
+results_df.to_csv(csv_file_path, index=False)
+
+print(f"Results have been saved to {csv_file_path}")
+
 ```

### 2024-02-29 ollama_query.py

@@ -1,0 +1,18 @@
+import requests
+import json
+
+url = "http://localhost:11434/api/generate"
+
+headers = {"Content-Type":"application/json"｝
+
+data = {"model": "llama2", "prompt": "Why is the sky blue?", "stream": False}
+
+response = requests.post(url, headers=headers, data=json.dumps(data))
+
+if response.status_code == 200:
+  response_text = response.text
+  data = json. loads (response_text)
+  actual_response = data[ "response" ]
+  print(actual_response )
+else:
+  print( "Error:", response.status_code, response.text)

### 2024-02-29 paper.qmd
upload the results of the call to an LLM

--- 2024-02-25 paper.qmd
@@
 # Read the CSV files
+import pandas as pd
 spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
@@
 import numpy as np
+from datetime import datetime 
 def season_to_date(season):
@@
 spells1.loc[mask, 'Finish'] = spells1.loc[mask,'contract_expiry'].apply(season_to_date)
-#spells1[spells1['Finish'].isna()].value_counts()
 spells1['Finish'].isna().value_counts()
+
+```
+```{python}
+#spells1['spell_in_days']=spells1['Finish']-spells1['Start']
+#spells1['spell_in_days']
+import csv
+team_names=spells1['club'].unique()
+# Convert the Series to a DataFrame
+teams_df = pd.DataFrame(team_names,columns=['TeamName'])
+teams_df.to_csv('teams.csv')
+```
+
+```{python}
+team_names
 ```

### 2024-03-02 paper.qmd
some updates on mac for data summary

--- 2024-02-29 paper.qmd
@@
 library(purrr)
-spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+#spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
+
 # Define season_to_date() function here
@@
 
-data_helper <- spells1 |>
+data_helper <- spells |>
   mutate(row_id=row_number()) |>
@@
   mutate(row_id=row_number()) |>
-  left_join(data_helper, by="row_id") |>
+  left_join(data_helper |> select(-Finish), by="row_id") |>
   mutate(Start = as.Date(Start),
@@
   mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
+spells |> distinct(name,club,Finish) |> nrow()
+# find duplicates for name,club,Finish
+spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
+# remove duplicates
+spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
+spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
+spell |> filter(Finish-Start>0) -> spell
+```
 
+The raw data from transfrmarkt is then cleaned and processed to create a raw dataset of manager spells. The dataset contains the following columns:
+
+- `name`: The name of the person in charge
+- `club`: The club the manager was in charge of
+- `position`: The position of the person in charge
+- `Start`: The start date of the spell
+- `Finish`: The end date of the spell
+- `days_in_charge`: The number of days the manager was in charge of the club
+- `season_start`: The start of the season the spell ended
+
+```{r}
+#| label: fig-annual-spell-count
+#| fig-cap: "Annual count of manager spell ending"
+library(ggplot2)
+library(dplyr)
+# create plot of annual count of spells using a count of finishes per season assume season starts in August
+spell |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
+  count(season_start) |> 
+  ggplot(aes(x = season_start, y = n)) +
+  geom_col(width = 0.5) +
+  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
+  theme_minimal() -> spell_count
+plotly::ggplotly(spell_count)
+```
+
+```{r}
+```
+
+```{bash}
+#!/bin/bash
+
+# Define a function to make an HTTP request to the API and parse the response
+function api_call() {
+  local club_name="$1"
+  local year_end_of_season="$2"
+  local response=$(curl -s -H "Content-Type: application/json" \
+    --data '{"model": "llama2", "prompt": "Which country is the club 
+${club_name} from? What is its division level based on the year 
+${year_end_of_season}?"}' http://localhost:11434/api/generate)
+  echo "Processing club ${club_name} (${year_end_of_season})"
+  echo "${response}" >> responses.csv
+}
+
+# Read the input CSV file with clubs and end of season dates using csvparse
+input_file="input.csv"
+output_file="output.csv"
+IFS=$'\n'
+mapfile -t clubs < <(csplit ${input_file} '{printf "%s\n" %${0}}}')
+unset IFS
+declare -a clubs_array=(${clubs[@]})
+declare -a years_array=()
+for i in $(seq 0 ${#clubs_array[*]}-1); do
+  IFS=',' read -r club_name year < "${input_file}" || continue
+  years_array+=("${year}")
+done
+unset IFS
+
+# Loop over the clubs and call the API for each one with its respective end 
+of season year
+for ((i = 0; i < ${#clubs_array[@]}; i++)); do
+  local club_name="${clubs_array[$i]}"
+  local year="${years_array[$i]}"
+  api_call "${club_name}" "${year}"
+done
+
+echo "Done processing all clubs. Total responses processed: $(wc -l < 
+responses.csv)"
 ```
@@
 generator = pipeline("text-generation")
-# Load model directly
-# from transformers import AutoTokenizer, AutoModelForCausalLM
-# 
-# tokenizer = AutoTokenizer.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")
-# model = AutoModelForCausalLM.from_pretrained("mistralai/Mixtral-8x7B-Instruct-v0.1")  
-# Use a pipeline as a high-level helper
-#from transformers import pipeline
-#pipe = pipeline("text-generation", model="mistralai/Mixtral-8x7B-Instruct-v0.1")
 

### 2024-03-03 paper.qmd
update

@@
 
-## Manager spell profiles
+## Manager spell
 
@@
 # find duplicates for name,club,Finish
-spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
+#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
 # remove duplicates
-spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
-spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
-spell |> filter(Finish-Start>0) -> spell
+spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
+
 ```
@@
 
-- `name`: The name of the person in charge
-- `club`: The club the manager was in charge of
-- `position`: The position of the person in charge
-- `Start`: The start date of the spell
-- `Finish`: The end date of the spell
+-   `name`: The name of of staff member
+-   `club`: The club of the staff member
+-   `position`: The position of the staff member
+-   `appointed`: The start date of the spell
+-   `contract_expiry`: The end date of the spell
 -   `days_in_charge`: The number of days the manager was in charge of the club
-- `season_start`: The start of the season the spell ended
+-   `wins`: Number of wins for spell
+-   `draws`: Number of draws for spell
+-   `losses`: Number of losses for spell
+-   `players_used`: Number of players used in the spell
+-   `avg_goals_for`: Average goals scored per game
+-   `avg_goals_against`: Average goals conceded per game
+-    `ppm`: Points per match
+
+```{r}
+#|label: fig-managertype
+#|fig-cap: "Word cloud of manager types"
+
+# Use the wordcloud package to create a word cloud of manager types using position column
+library(wordcloud)
+library(tm)
+library(SnowballC)
+terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
+  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
+  "1.FC Köln U17","1.FC Köln Yth.",
+  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
+  "Hertha BSC","F. Düsseldorf",
+  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
+  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
+  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
+  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
+  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
+paste0("(",paste(terms_to_remove,collapse="|"),")")  -> remove_terms
+spells |>
+  str_remove(position,terms_to_remove[1]) %>%
+  {table(.$position)}
+
+spells |> mutate(
+    staff_position = trimws(tolower(position)),
+    staff_position = ifelse(staff_position=="manager","manager",staff_position),
+    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
+    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) -> spells
+
+table(spells$staff_position[!is.na(spells$staff_position)]) |> sort(decreasing = TRUE)
+```
+
+```{r}
+
+VCorpus <- Corpus(VectorSource(spells$position[!is.na(spells$position)]))
+terms_to_remove <-c('Al-Ahli (UAE)','')
+# Copy text to clipboard on Linux
+text <- unique(spells$position[!is.na(spells$position)])
+write(text, "| xclip -selection clipboard")
+
+table(spells$position[!is.na(spells$position)])
+VCorpus <- VCorpus |>
+  tm_map(content_transformer(tolower)) |> 
+  tm_map(removePunctuation) |> 
+  tm_map(removeNumbers) |> 
+  tm_map(removeWords, stopwords("en")) |> 
+  tm_map(stripWhitespace) |> 
+  TermDocumentMatrix() |> 
+  as.matrix() |> 
+  colSums() |> 
+  sort(decreasing = TRUE) 
+wordcloud(words = names(VCorpus), freq = VCorpus, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"))
+```
 

### 2024-03-04 paper.qmd
standardise position text

--- 2024-03-02 paper.qmd
@@
 
-- `name`: The name of the person in charge
-- `club`: The club the manager was in charge of
-- `position`: The position of the person in charge
-- `Start`: The start date of the spell
-- `Finish`: The end date of the spell
+-   `name`: The name of of staff member
+-   `club`: The club of the staff member
+-   `position`: The position of the staff member
+-   `appointed`: The start date of the spell
+-   `contract_expiry`: The end date of the spell
 -   `days_in_charge`: The number of days the manager was in charge of the club
-- `season_start`: The start of the season the spell ended
+-   `wins`: Number of wins for spell
+-   `draws`: Number of draws for spell
+-   `losses`: Number of losses for spell
+-   `players_used`: Number of players used in the spell
+-   `avg_goals_for`: Average goals scored per game
+-   `avg_goals_against`: Average goals conceded per game
+-    `ppm`: Points per match
+
+```{r}
+#|label: fig-managertype
+#|fig-cap: "Word cloud of manager types"
+
+# Use the wordcloud package to create a word cloud of manager types using position column
+#library(wordcloud)
+#library(tm)
+#library(SnowballC)
+terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
+  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
+  "1.FC Köln U17","1.FC Köln Yth.",
+  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
+  "Hertha BSC","F. Düsseldorf",
+  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
+  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
+  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
+  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
+  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
+#paste0("(",paste(terms_to_remove,collapse="|"),")")  -> remove_terms
+# spells %>%
+#   mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) %>%
+#   ungroup() %>%
+#   {table(.$position)} %>% sort(decreasing = TRUE) %>% head(20)
+```
+
+```{r}
+library(wordcloud)
+library(kableExtra)
+spells %>%
+  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
+spells |> mutate(
+    staff_position = trimws(tolower(position)),
+    staff_position = ifelse(staff_position=="manager","manager",staff_position),
+    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
+    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
+  {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
+  # make the frequency table into a data frame
+  as.data.frame() |>
+  # rename the columns
+  rename("staff_position" = "Var1", "n" = "Freq") |>
+  # order the data frame by the frequency
+  arrange(desc(n)) |>
+  head(20) |>
+  kbl() |>
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
+```
+
+```{r}
+
+```
 

### 2024-03-05 paper.qmd
updating the LLM work

--- 2024-03-02 paper.qmd
@@
   mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
-spells |> distinct(name,club,Finish) |> nrow()
 # find duplicates for name,club,Finish
-spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
+#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
 # remove duplicates
-spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
-spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
-spell |> filter(Finish-Start>0) -> spell
+spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
+
 ```
@@
 
-- `name`: The name of the person in charge
-- `club`: The club the manager was in charge of
-- `position`: The position of the person in charge
-- `Start`: The start date of the spell
-- `Finish`: The end date of the spell
+-   `name`: The name of of staff member
+-   `club`: The club of the staff member
+-   `position`: The position of the staff member
+-   `appointed`: The start date of the spell
+-   `contract_expiry`: The end date of the spell
 -   `days_in_charge`: The number of days the manager was in charge of the club
-- `season_start`: The start of the season the spell ended
+-   `wins`: Number of wins for spell
+-   `draws`: Number of draws for spell
+-   `losses`: Number of losses for spell
+-   `players_used`: Number of players used in the spell
+-   `avg_goals_for`: Average goals scored per game
+-   `avg_goals_against`: Average goals conceded per game
+-    `ppm`: Points per match
+
+```{r}
+
+```
+
+```{r}
+#|label: tbl-managertype
+#| tbl-cap: "Manager types"
+library(kableExtra)
+terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
+  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
+  "1.FC Köln U17","1.FC Köln Yth.",
+  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
+  "Hertha BSC","F. Düsseldorf",
+  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
+  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
+  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
+  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
+  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
+spells %>%
+  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
+spells |> mutate(
+    staff_position = trimws(tolower(position)),
+    staff_position = ifelse(staff_position=="manager","manager",staff_position),
+    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
+    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
+  {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
+  # make the frequency table into a data frame
+  as.data.frame() |>
+  # rename the columns
+  rename("staff_position" = "Var1", "n" = "Freq") |>
+  # order the data frame by the frequency
+  arrange(desc(n)) |>
+  head(20) |>
+  kable(col.names=c("Staff Role","Number")) |>
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
+```
 
@@
 # create plot of annual count of spells using a count of finishes per season assume season starts in August
-spell |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
+spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
   count(season_start) |> 
@@
 ```{r}
-```
-
-```{bash}
-#!/bin/bash
-
-# Define a function to make an HTTP request to the API and parse the response
-function api_call() {
-  local club_name="$1"
-  local year_end_of_season="$2"
-  local response=$(curl -s -H "Content-Type: application/json" \
-    --data '{"model": "llama2", "prompt": "Which country is the club 
-${club_name} from? What is its division level based on the year 
-${year_end_of_season}?"}' http://localhost:11434/api/generate)
-  echo "Processing club ${club_name} (${year_end_of_season})"
-  echo "${response}" >> responses.csv
-}
-
-# Read the input CSV file with clubs and end of season dates using csvparse
-input_file="input.csv"
-output_file="output.csv"
-IFS=$'\n'
-mapfile -t clubs < <(csplit ${input_file} '{printf "%s\n" %${0}}}')
-unset IFS
-declare -a clubs_array=(${clubs[@]})
-declare -a years_array=()
-for i in $(seq 0 ${#clubs_array[*]}-1); do
-  IFS=',' read -r club_name year < "${input_file}" || continue
-  years_array+=("${year}")
-done
-unset IFS
-
-# Loop over the clubs and call the API for each one with its respective end 
-of season year
-for ((i = 0; i < ${#clubs_array[@]}; i++)); do
-  local club_name="${clubs_array[$i]}"
-  local year="${years_array[$i]}"
-  api_call "${club_name}" "${year}"
-done
-
-echo "Done processing all clubs. Total responses processed: $(wc -l < 
-responses.csv)"
 ```

### 2024-03-05 LLM-work/loop.sh

@@ -1,0 +1,45 @@
+#!/bin/bash
+
+# Function to make a call to the local LLM and parse the response
+api_call() {
+  local club_name="$1"
+  local end_of_spell="$2" # Assuming this variable is provided
+  local temp_output="temp_response.txt" # Temporary file to store LLM response
+  
+  # Concatenate all questions into a single prompt
+  local prompt="""
+  Question 1: Which league did ${club_name} play in on ${end_of_spell}? 
+  Question 2: Categorise the team name ${club_name} into one of the following: 
+  First Team 
+  Youth Team 
+  Reserve Team 
+  Womens Team 
+  International Team
+  Other
+  Question 3: Given this ${end_of_spell} date, what division was ${club_name} in?
+  """
+  
+  # Call the local LLM model
+  echo "$prompt" | ollama run llama2 > "$temp_output"
+  local response=$(cat "$temp_output")
+  
+  echo "Processing club ${club_name} (${end_of_spell}})"
+  
+  # Assuming the response can be directly appended. Adjust based on the actual output format
+  echo "${club_name},${end_of_spell},\"${response}\"" >> "${output_file}"
+  
+  # Cleanup temporary file
+  rm -f "$temp_output"
+}
+
+input_file="input.csv"
+output_file="output.csv"
+echo "club_name,end_of_spell,API Response" > "${output_file}"
+
+while IFS=',' read -r club_name end_of_spell; do
+  if [[ -n "$club_name" && -n "$end_of_spell" ]]; then
+    api_call "$club_name" "$end_of_spell"
+  fi
+done < "${input_file}"
+
+echo "Done processing all clubs. Total responses processed: $(( $(wc -l < "${output_file}") - 1 ))"

### 2024-03-05 LLM-work/preprocessing.R

@@ -1,0 +1,69 @@
+library(dplyr)
+library(purrr)
+#spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
+
+# Define season_to_date() function here
+season_to_date <- function(season) {
+  if (is.na(season) | length(gsub("/", "", season)) == 0) {
+    return(NA_real_)
+  }
+  
+  parts <- strsplit(season, "/")[[1]]
+  month <- as.numeric(parts[2])
+  if (month < 8) {
+    year <- paste0("20", substr(parts[1], 1, 2))
+  } else {
+    year <- paste0("19", substr(parts[1], 1, 2))
+  }
+  
+  date_str <- paste0("01/08/", year)
+  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
+}
+
+data_helper <- spells |>
+  mutate(row_id=row_number()) |>
+  filter(is.na(Finish)&contract_expiry!="-") |>
+  select(contract_expiry, Finish,row_id)
+data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
+spells |>
+  mutate(row_id=row_number()) |>
+  left_join(data_helper |> select(-Finish), by="row_id") |>
+  mutate(Start = as.Date(Start),
+         Finish = as.Date(Finish)) |>
+  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
+# find duplicates for name,club,Finish
+#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
+# remove duplicates
+spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
+library(kableExtra)
+terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
+                     "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
+                     "1.FC Köln U17","1.FC Köln Yth.",
+                     "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
+                     "Hertha BSC","F. Düsseldorf",
+                     "Velez Mostar","SSV Reutlingen","FV Ravensburg",
[…]

### 2024-03-12 paper.qmd
Update paper.qmd

@@
 library (tidybayes)
-reticulate::use_condaenv("pymc")
+#reticulate::use_condaenv("pymc")
 
@@
     staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
+    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) -> spells
+
+spells %>%
   {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
@@
 # create plot of annual count of spells using a count of finishes per season assume season starts in August
-spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
-  count(season_start) |> 
+spells |> 
+  mutate(youth_team = ifelse(str_detect(club, "[A-Z][0-9]{2}|Yth."), "Yes", "No")) -> spells
+
+# Create a list of the worlds countries in lowercase
+countries <- c("albania", "andorra", "austria", "belarus", "belgium", "bosnia-herzegovina", "bulgaria", "croatia", "cyprus", "czech-republic", "denmark", "estonia", "faroe-islands", "finland", "france", "germany", "gibraltar", "greece", "hungary", "iceland", "ireland", "italy", "kosovo", "latvia", "liechtenstein", "lithuania", "luxembourg", "malta", "moldova", "montenegro", "netherlands", "north-macedonia", "northern-ireland", "norway", "poland", "portugal", "romania", "russia", "san-marino", "scotland", "serbia", "slovakia", "slovenia", "spain", "sweden", "switzerland", "turkey", "ukraine", "wales", "england")
+
+# find the name of a country in the club name
+spells |> 
+  mutate(country = str_extract(club, "([A-Z][a-z]+)")) |> 
+  filter(!is.na(country)) |> 
+  count(country) |> 
+  arrange(desc(n)) |> 
+  head(20) |> 
+  kable(col.names=c("Country","Number")) |> 
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
+
+# plot the annual count of spells using a count of finishes per season assume season starts in August and condition on youth_team
+spells |> 
+  filter(staff_position=="manager") |> 
+  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
+  group_by(season_start,youth_team) |>
+  count(season_start)
+
+|> 
   ggplot(aes(x = season_start, y = n)) +
   geom_col(width = 0.5) +
-  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
+  labs(title = "", x = "Season", y = "Number of spells") +
   theme_minimal() -> spell_count
+
 plotly::ggplotly(spell_count)
@@
 ```{r}
+
 ```

### 2024-04-08 paper_new.qmd
updated

--- 2024-03-05 paper.qmd
@@
 #spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
-
-# Define season_to_date() function here
-season_to_date <- function(season) {
-  if (is.na(season) | length(gsub("/", "", season)) == 0) {
-    return(NA_real_)
-  }
-
-  parts <- strsplit(season, "/")[[1]]
-  month <- as.numeric(parts[2])
-   if (month < 8) {
-     year <- paste0("20", substr(parts[1], 1, 2))
-   } else {
-     year <- paste0("19", substr(parts[1], 1, 2))
-   }
-
-  date_str <- paste0("01/08/", year)
-  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
-}
-
-data_helper <- spells |>
-  mutate(row_id=row_number()) |>
-  filter(is.na(Finish)&contract_expiry!="-") |>
-  select(contract_expiry, Finish,row_id)
-data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
-spells |>
-  mutate(row_id=row_number()) |>
-  left_join(data_helper |> select(-Finish), by="row_id") |>
-  mutate(Start = as.Date(Start),
-         Finish = as.Date(Finish)) |>
-  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
-# find duplicates for name,club,Finish
-#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
-# remove duplicates
-spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
-
+spells <- readRDS("raw_data/manager_spells_from_manager_urls.rds")
+names(spells)[20:22]<-c("Country","Division", "Full Name")
 ```
@@
 library(kableExtra)
-terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
-  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
-  "1.FC Köln U17","1.FC Köln Yth.",
-  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
-  "Hertha BSC","F. Düsseldorf",
-  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
-  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
-  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
-  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
-  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
 spells %>%
-  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
-spells |> mutate(
-    staff_position = trimws(tolower(position)),
-    staff_position = ifelse(staff_position=="manager","manager",staff_position),
-    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
-    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
-    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
   {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
@@
 # create plot of annual count of spells using a count of finishes per season assume season starts in August
-spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
+spells |> 
+  mutate(youth_team = ifelse(str_detect(club, "[A-Z][0-9]{2}|Yth.|Youth"), "Yes", "No")) -> spells
+
+# create a list of european countries
+european_countries <- c("albania", "andorra", "austria", "belarus", "belgium", "bosnia-herzegovina", "bulgaria", "croatia", "cyprus", "czech-republic", "denmark", "estonia", "faroe-islands", "finland", "france", "germany", "gibraltar", "greece", "hungary", "iceland", "ireland", "italy", "kosovo", "latvia", "liechtenstein", "lithuania", "luxembourg", "malta", "moldova", "montenegro", "netherlands", "north-macedonia", "northern-ireland", "norway", "poland", "portugal", "romania", "russia", "san-marino", "scotland", "serbia", "slovakia", "slovenia", "spain", "sweden", "switzerland", "turkey", "ukraine", "wales", "england")
+# Create a list of north and south american countries
+north_american_countries <- c("canada", "mexico", "united-states","USA")
+# list of central american countries
+central_american_countries <- c("belize", "costa-rica", "el-salvador", "guatemala", "honduras", "nicaragua", "panama")
+south_american_countries <- c("argentina", "bolivia", "brazil", "chile", "colombia", "ecuador", "paraguay", "peru", "uruguay", "venezuela")
+# Create list of australiasian countries
+australasian_countries <- c("australia", "fiji", "new-zealand", "papua-new-guinea", "solomon-islands", "vanuatu")
+# Create list of african countries
+african_countries <- c("algeria", "angola", "benin", "botswana", "burkina-faso", "burundi", "cameroon", "cape-verde", "central-african-republic", "chad", "comoros", "congo", "djibouti", "egypt", "equatorial-guinea", "eritrea", "eswatini", "ethiopia", "gabon", "gambia", "ghana", "guinea", "guinea-bissau", "ivory-coast", "kenya", "lesotho", "liberia", "libya", "madagascar", "malawi", "mali", "mauritania", "mauritius", "morocco", "mozambique", "namibia", "niger", "nigeria", "rwanda", "sao-tome-and-principe", "senegal", "seychelles", "sierra-leone", "somalia", "south-africa", "south-sudan", "sudan", "tanzania", "togo", "tunisia", "uganda", "zambia", "zimbabwe")
+# Create list of asian countries
+asian_countries <- c("afghanistan", "armenia", "azerbaijan", "bahrain", "bangladesh", "bhutan", "brunei", "cambodia", "china", "east-timor", "georgia", "india", "indonesia", "iran")
+# Create a list of countries that are not in the above lists
+other_countries <- c("anguilla", "antigua-and-barbuda", "aruba", "bahamas", "barbados", "bermuda", "british-virgin-islands", "cayman-islands", "curacao", "dominica", "falkland-islands", "greenland", "grenada", "guadeloupe", "haiti", "jamaica", "martinique", "montserrat", "netherlands-antilles", "puerto-rico", "saint-kitts-and-nevis", "saint-lucia", "saint-vincent-and-the-grenadines", "sint-maarten", "trinidad-and-tobago", "turks-and-caicos-islands", "us-virgin-islands")
+all_countries <- c(european_countries, north_american_countries, central_american_countries, south_american_countries, australasian_countries, african_countries, asian_countries, other_countries)
+spells |> mutate(national_team = if_else(tolower(club) %in% all_countries,"Yes","No")) -> spells
+# plot the annual count of spells using a count of finishes per season assume season starts in August and condition on youth_team
+spells |> 
+  filter(staff_position=="manager" & national_team =="No" & youth_team=="No") |> 
+  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
+  group_by(season_start,national_team) |>
   count(season_start)  |> 
-  ggplot(aes(x = season_start, y = n)) +
+  ggplot(aes(x = season_start, y = n, fill=national_team)) +
   geom_col(width = 0.5) +
-  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
+  labs(title = "Manager-Club spells per annum", x = "Season Start Year", y = "Number of Turnovers") +
   theme_minimal() -> spell_count
@@
 ```{r}
+spells |> 
+  filter(staff_position=="manager" & national_team =="No" & youth_team=="No") |> 
+  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
+  group_by(season_start,national_team) |>
+  count(season_start)  |> 
+  ggplot(aes(x = season_start, y = n, fill=national_team)) +
+  geom_col(width = 0.5) +
+  labs(title = "Manager-Club spells per annum", x = "Season Start Year", y = "Number of Turnovers") +
+  theme_minimal() -> spell_count
+plotly::ggplotly(spell_count)
 ```
 
-```{python}
-import pandas as pd
-import time
-from transformers import pipeline
-
-generator = pipeline("text-generation")
-
-# Load the unique club names from the CSV file
-spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-club_names=spells1['club'].unique()
-
-# Initialize an empty list to store the results
-results = []
-
-# Iterate over the array of club names and add a timer for each iteration
-start_time = time.time()
-for club in club_names:
-    # Prepare the prompt for the model
-    prompt = f"Provide information about the soccer club {club}: its country of origin,  division level, and whether it is a first  team or a youth team."
-
-    # Generate the response using the model
-    start = time.time()
-    responses=generator(prompt)
-
-    # Assuming the first (or only) response is what we're interested in
-    response_text = responses[0]
-
-    # Store the response, elapsed time for this iteration and total elapsed time in our results list
-    results.append({'ClubName': club, 'Information': response_text, 'ElapsedTimePerIteration': time.time() - start, 
-'TotalElapsedTime': time.time() - start_time})
-
-# Convert the results list to a DataFrame
-import pandas as pd
-results_df = pd.DataFrame(results)
-
-# Display the DataFrame to verify the results
-print(results_df)
-
-# Specify the file path for the CSV file
-csv_file_path = 'soccer_clubs_information_hf.csv'
-
-# Save the DataFrame to a CSV file
-results_df.to_csv(csv_file_path, index=False)
-
-print(f"Results have been saved to {csv_file_path}")
-
+```{r}
+spells |>
 ```
-
 # Methodology

### 2024-04-08 LLM-work/preprocessing.R

@@ -1,6 +1,6 @@
 library(dplyr)
 library(purrr)
-#spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
+library(stringr)
 spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
 
 # Define season_to_date() function here
@@ -36,7 +36,6 @@ spells |>
 #spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
 # remove duplicates
 spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
-library(kableExtra)
 terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
                      "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
                      "1.FC Köln U17","1.FC Köln Yth.",
@@ -64,6 +63,12 @@ spells |> mutate(
   staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
   staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position))-> spells
 
+#spells |> distinct(club,Finish) |> select(club,Finish) |> rename("club_name"="club","end_of_spell"="Finish") |> write_csv("LLM-work/input.csv")
 
-spells |> distinct(club,Finish) |> rename("club_name"="club","end_of_spell"="Finish") |> head(10) |> write_csv("LLM-work/test_input.csv")
-spells |> distinct(club,Finish) |> select(club,Finish) |> rename("club_name"="club","end_of_spell"="Finish") |> write_csv("LLM-work/input.csv")
+llm<-read.csv(file = "LLM-work/outputadj_parsed.csv")
+spells |>
+  mutate(mergevar=as.character(Finish)) |>
+  left_join(llm, by=c("club"="club_name","mergevar"="end_of_spell")) |>
+  select(-mergevar&-contract_expiry.x) |> 
+  rename("contract_expiry"="contract_expiry.y") |>
+  saveRDS("raw_data/manager_spells_from_manager_urls.rds")

### 2024-04-10 paper_new.qmd
update with cleaning

@@
 # plot the annual count of spells using a count of finishes per season assume season starts in August and condition on youth_team
-spells |> 
-  filter(staff_position=="manager" & national_team =="No" & youth_team=="No") |> 
-  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
-  group_by(season_start,national_team) |>
-  count(season_start)  |> 
-  ggplot(aes(x = season_start, y = n, fill=national_team)) +
-  geom_col(width = 0.5) +
-  labs(title = "Manager-Club spells per annum", x = "Season Start Year", y = "Number of Turnovers") +
-  theme_minimal() -> spell_count
-plotly::ggplotly(spell_count)
 ```
@@
   count(season_start)  |> 
-  ggplot(aes(x = season_start, y = n, fill=national_team)) +
+  ggplot(aes(x = season_start, y = n)) +
   geom_col(width = 0.5) +
@@
 ```{r}
-spells |>
+library(clipr)
+unique(spells$Country) |> write_clip()
 ```
+
+```{r}
+# Assuming the LLM output is stored in a variable called 'llm_output'
+categories <- unique(spells$Country)
+
+# Remove leading/trailing whitespace and convert to lowercase
+categories <- trimws(categories)
+categories <- tolower(categories)
+
+# Remove any leading/trailing punctuation marks
+categories <- gsub("^[[:punct:]]+|[[:punct:]]+$", "", categories)
+
+# Replace ' - ' and ' . ' with '.'
+categories <- gsub(" - | \\. ", ".", categories)
+
+# Replace 'not applicable', 'none', 'unknown', 'not found', 'not available', 'n/a' with NA
+categories[categories %in% c("not applicable", "none", "unknown", "not found", "not available", "n/a","","0")] <- NA
+
+# Categorize responses indicating LLM cannot find answer
+llm_cannot_answer <- grepl("^i am not|^i cannot|^i don't|^i am just an ai|^i'm just an ai", categories)
+categories[llm_cannot_answer] <- "LLM cannot find answer"
+
+# Remove rows with NA values
+categories <- categories[!is.na(categories)]
+
+# Remove duplicate categories
+categories <- unique(categories)
+
+# Sort the categories alphabetically
+categories <- sort(categories)
+categories <- trimws(categories)
+# Print the cleaned categories
+unique(categories) |> write_clip()
+```
+
+```{r}
+library(countries)
+list_countries() |> length()
+```
+
+```{r}
+# Assuming the list is stored in a variable called 'categories'
+countries <- gsub("^.*\\b(\\w+)\\.*$", "\\1", spells$Country, perl = TRUE)
+
+# Replace common non-country phrases with NA
+non_countries <- c("based on my training data", "based on training data", "LLM cannot find answer", "none", "not applicable", "not found in my training data", "not sure", 
+                   "unknown", "soccer", "tennis", "world cup", "football soccer", "northern", 
+                   "rome", "soccer football", "west africa", "south america", "central america", 
+                   "eastern europe", "north macedonia", "fifa", "uefa", "asia", "eu", "uefa european football association","uefa european", "eurozone", "caribbean", "cricket", "\\bi'm.*", "\\bi have.*", "\\bi cannot.*",
+                   "\\bi don't.*", "\\bi couldn't.*", "\\bna\\b", "\\bn/a\\b", "i can","\\bi am not aware","i am", "answer:", "africa", "europe", 
+                   "middle east", "east germany", "soviet union", "uae", "uk", "usa", "world")
+countries[countries %in% non_countries] <- NA
+
+# Remove any leading/trailing whitespace
+countries <- trimws(countries)
+
+# Replace empty strings with NA
+countries[countries == ""] <- NA
+
+# Merge similar country names
+# Create a named vector for country name mappings
+country_mappings <- c(
+  "_England_" = "England",
+  "_Belgium_" = "Belgium",
+  "_Germany_" = "Germany",
+  "_Italy_" = "Italy",
+  "_Serbia_" = "Serbia",
+  "England -" = "England",
+  "States" = "United States",
+  "United States -" = "United States",
+  "Kingdom" = "United Kingdom",
+  "United Kingdom UK -" = "United Kingdom",
+  "Democratic Republic of Congo" = "Democratic Republic of the Congo",
+  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
+  "Soviet Union" = "Russia",
+  "Soviet Union former" = "Russia",
+  "Soviet Union formerly" = "Russia",
+  "Russia formerly Soviet Union" = "Russia",
+  "Yugoslavia" = "Serbia",
+  "Yugoslavia now Serbia" = "Serbia",
+  "Yugoslavia or SFR Yugoslavia" = "Serbia",
+  "Serbia formerly Yugoslavia" = "Serbia",
+  "East Germany" = "Germany",
+  "East Germany GDR" = "Germany",
+  "East Germany Germany" = "Germany",
+  "East Germany Germany Democratic Republic" = "Germany",
+  "Macedonia" = "North Macedonia",
+  "Macedonia formerly known as the Republic of Macedonia" = "North Macedonia",
+  "Burma" = "Myanmar",
+  "Myanmar Burma" = "Myanmar",
+  "Congo" = "Democratic Republic of the Congo",
+  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
+  "Ivoire" = "Ivory Coast",
+  "Holland" = "Netherlands",
+  "Holland Netherlands" = "Netherlands",
+  "United Arab Emirates UAE" = "United Arab Emirates",
+  "UAE United Arab Emirates" = "United Arab Emirates",
+  "United Kingdom UK" = "United Kingdom",
+  "UK" = "United Kingdom",
+  "ANDORA" = "Andorra",
+  "Faso" = "Burkina Faso",
+  "Rica" = "Costa Rica",
+  "Salvador" = "El Salvador"
+)
+
+# Merge similar country names using the country_mappings vector
+for (i in seq_along(countries)) {
+  if (countries[i] %in% names(country_mappings)) {
+    countries[i] <- country_mappings[countries[i]]
+  }
+}
+
+# Handle historical country names
+countries[countries == "Czechoslovakia"] <- NA  # Czechoslovakia no longer exists, split into Czech Republic and Slovakia
+
+# Remove additional non-country values
+non_countries <- c("International", "UEFA", "FIFA", "UEFA European", "European", "AFC", "GDR", "EU", "Eurozone", "UEFA European Football Union")
+countries[countries %in% non_countries] <- NA
+
+# Print the extracted country names
+#countries |> table() |> sort(decreasing = TRUE)
+unique(countries) |> write_clip()
+```
+
+```{r})
+```
+
+```{r}
+table(countries) |> sort(decreasing = TRUE)
+```
+
 # Methodology

### 2024-05-15 LLM-work/LLM_data_generator.sh
some more llm-work

@@ -1,0 +1,49 @@
+#!/bin/bash
+
+# Counter
+counter=0
+
+# Read the prompt template from prompt_template.txt
+prompt_template=$(cat prompt_template.txt)
+   
+# Function to make a call to the local LLM and parse the response
+api_call() {
+    local club_name="$1"
+    local end_of_spell="$2"
+    local temp_output="temp_response.txt"  # Temporary file to store LLM response
+
+    # Replace placeholders in the prompt template with local variables
+    local prompt="${prompt_template//${club_name}/$club_name}"
+    prompt="${prompt//${end_of_spell}/$end_of_spell}"
+
+    # Call the local LLM model
+    echo "$prompt" | ollama run llama3 > "$temp_output"
+
+    local response=$(cat "$temp_output")
+
+    # Increment counter
+    ((counter++))
+
+    echo "Processing club ${club_name} (${end_of_spell}) - ${counter} of ${total_lines} processed"
+    ## echo "${prompt}"	
+    # Append the JSON response to the master output file
+    echo "$response" >> master_output.jsonl
+}
+
+# Read input from a file or stdin
+while IFS= read -r line || [ -n "$line" ]; do
+    # Parse the input line to extract club_name and end_of_spell
+    club_name=$(echo "$line" | cut -d ',' -f 1)
+    end_of_spell=$(echo "$line" | cut -d ',' -f 2)
+
+    # Call the api_call function with the extracted variables
+    api_call "$club_name" "$end_of_spell"
+done < "${1:-/dev/stdin}"
+
+# Create a valid JSON array from the JSONL file
+echo "[" > master_output.json
+sed "$!s/$/,/" master_output.jsonl >> master_output.json
+echo "]" >> master_output.json
+
+# Convert JSON to CSV using jq
+jq -r '["club_name", "end_of_spell", "country", "division", "full_name", "country_confidence", "division_confidence", "full_name_confidence"], (.[] | [.club_name, .end_of_spell, .country, .division, .full_name, .country_confidence, .division_confidence, .full_name_confidence]) | @csv' master_output.json > master_output.csv

### 2024-05-15 LLM-work/loop_w_counter.sh

@@ -24,7 +24,7 @@ api_call() {
   """
   
   # Call the local LLM model
-  echo "$prompt" | ollama run llama2 > "$temp_output"
+  echo "$prompt" | ollama run llama3 > "$temp_output"
   local response=$(cat "$temp_output")
   
   # Increment counter

### 2024-05-15 paper.qmd

--- 2024-03-05 paper.qmd
@@
 #spells <- read.csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
-
-# Define season_to_date() function here
-season_to_date <- function(season) {
-  if (is.na(season) | length(gsub("/", "", season)) == 0) {
-    return(NA_real_)
-  }
-
-  parts <- strsplit(season, "/")[[1]]
-  month <- as.numeric(parts[2])
-   if (month < 8) {
-     year <- paste0("20", substr(parts[1], 1, 2))
-   } else {
-     year <- paste0("19", substr(parts[1], 1, 2))
-   }
-
-  date_str <- paste0("01/08/", year)
-  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
-}
-
-data_helper <- spells |>
-  mutate(row_id=row_number()) |>
-  filter(is.na(Finish)&contract_expiry!="-") |>
-  select(contract_expiry, Finish,row_id)
-data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
-spells |>
-  mutate(row_id=row_number()) |>
-  left_join(data_helper |> select(-Finish), by="row_id") |>
-  mutate(Start = as.Date(Start),
-         Finish = as.Date(Finish)) |>
-  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
-# find duplicates for name,club,Finish
-#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
-# remove duplicates
-spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
-
+spells <- readRDS("raw_data/manager_spells_from_manager_urls.rds")
 ```
@@
 # create plot of annual count of spells using a count of finishes per season assume season starts in August
-spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
+spells |> 
+  mutate(youth_team = ifelse(str_detect(club, "[A-Z][0-9]{2}|Yth.|Youth"), "Yes", "No")) -> spells
+
+# create a list of european countries
+european_countries <- c("albania", "andorra", "austria", "belarus", "belgium", "bosnia-herzegovina", "bulgaria", "croatia", "cyprus", "czech-republic", "denmark", "estonia", "faroe-islands", "finland", "france", "germany", "gibraltar", "greece", "hungary", "iceland", "ireland", "italy", "kosovo", "latvia", "liechtenstein", "lithuania", "luxembourg", "malta", "moldova", "montenegro", "netherlands", "north-macedonia", "northern-ireland", "norway", "poland", "portugal", "romania", "russia", "san-marino", "scotland", "serbia", "slovakia", "slovenia", "spain", "sweden", "switzerland", "turkey", "ukraine", "wales", "england")
+# Create a list of north and south american countries
+north_american_countries <- c("canada", "mexico", "united-states","USA")
+# list of central american countries
+central_american_countries <- c("belize", "costa-rica", "el-salvador", "guatemala", "honduras", "nicaragua", "panama")
+south_american_countries <- c("argentina", "bolivia", "brazil", "chile", "colombia", "ecuador", "paraguay", "peru", "uruguay", "venezuela")
+# Create list of australiasian countries
+australasian_countries <- c("australia", "fiji", "new-zealand", "papua-new-guinea", "solomon-islands", "vanuatu")
+# Create list of african countries
+african_countries <- c("algeria", "angola", "benin", "botswana", "burkina-faso", "burundi", "cameroon", "cape-verde", "central-african-republic", "chad", "comoros", "congo", "djibouti", "egypt", "equatorial-guinea", "eritrea", "eswatini", "ethiopia", "gabon", "gambia", "ghana", "guinea", "guinea-bissau", "ivory-coast", "kenya", "lesotho", "liberia", "libya", "madagascar", "malawi", "mali", "mauritania", "mauritius", "morocco", "mozambique", "namibia", "niger", "nigeria", "rwanda", "sao-tome-and-principe", "senegal", "seychelles", "sierra-leone", "somalia", "south-africa", "south-sudan", "sudan", "tanzania", "togo", "tunisia", "uganda", "zambia", "zimbabwe")
+# Create list of asian countries
+asian_countries <- c("afghanistan", "armenia", "azerbaijan", "bahrain", "bangladesh", "bhutan", "brunei", "cambodia", "china", "east-timor", "georgia", "india", "indonesia", "iran")
+
+# plot the annual count of spells using a count of finishes per season assume season starts in August and condition on youth_team
+spells |> 
+  filter(staff_position=="manager") |> 
+  mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |>
+  group_by(season_start,Answer_1) |>
   count(season_start)  |> 
-  ggplot(aes(x = season_start, y = n)) +
+  ggplot(aes(x = season_start, y = n, fill=Answer_1)) +
   geom_col(width = 0.5) +
-  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
+  labs(title = "", x = "Season", y = "Number of spells") +
   theme_minimal() -> spell_count

### 2024-05-15 paper_new.qmd

@@
 ```{r}
-library(clipr)
-unique(spells$Country) |> write_clip()
+# Install and load the 'countrycode' package if not already installed
+if (!requireNamespace("countrycode", quietly = TRUE)) {
+  install.packages("countrycode")
+}
+library(countries)
+
+# Get the list of country names
+countries <- list_countries()
+
+# Function to find the country in a text string
+find_country_in_text <- function(text, countries) {
+  for (country in countries) {
+    if (grepl(tolower(country), tolower(text))) {
+      return(country)
+    }
+  }
+  return('NA')
+}
+
+# Assuming your data is in a data frame named 'df' and the text strings are in a column named 'text'
+spells$matched_country <- sapply(spells$Country, function(x) find_country_in_text(x, countries))
+# sanity check
+table(spells$matched_country)
 ```
@@
 library(countries)
-list_countries() |> length()
+# write to to find partial matches within each string in a list of strings
+countries <- spells$Country
+countries <- tolower(countries)
+countries <- gsub(" - | \\. ", ".", countries)
+countries <- gsub("not applicable|none|unknown|not found|not available|n/a", NA, countries)
+countries <- gsub("i am not|i cannot|i don't|i am just an ai|i'm just an ai", "LLM cannot find answer", countries)
+countries <- countries[!is.na(countries)]
+country_list <-tolower(list_countries())
+sum(countries %in% tolower(list_countries()))
 ```

### 2024-05-15 LLM-work/LLM_data_generator.sh
Update LLM_data_generator.sh

@@ -10,28 +10,28 @@ prompt_template=$(cat prompt_template.txt)
 api_call() {
     local club_name="$1"
     local end_of_spell="$2"
-    local temp_output="temp_response.txt"  # Temporary file to store LLM response
+    local temp_output="temp_response.txt"
 
     # Replace placeholders in the prompt template with local variables
-    local prompt="${prompt_template//${club_name}/$club_name}"
-    prompt="${prompt//${end_of_spell}/$end_of_spell}"
+    local prompt=$(echo "$prompt_template" | sed "s/<club_name>/${club_name}/g; s/<end_of_spell>/${end_of_spell}/g")
 
     # Call the local LLM model
     echo "$prompt" | ollama run llama3 > "$temp_output"
-
     local response=$(cat "$temp_output")
 
     # Increment counter
     ((counter++))
-
     echo "Processing club ${club_name} (${end_of_spell}) - ${counter} of ${total_lines} processed"
-    ## echo "${prompt}"	
+
     # Append the JSON response to the master output file
     echo "$response" >> master_output.jsonl
 }
 
 # Read input from a file or stdin
-while IFS= read -r line || [ -n "$line" ]; do
+while IFS= read -r line || [[ -n "$line" ]]; do
+    # Skip the first line (header)
+    [[ "$line" =~ ^club_name,end_of_spell$ ]] && continue
+
     # Parse the input line to extract club_name and end_of_spell
     club_name=$(echo "$line" | cut -d ',' -f 1)
     end_of_spell=$(echo "$line" | cut -d ',' -f 2)

### 2024-05-15 LLM-work/LLM_data_generator.sh
Update LLM_data_generator.sh

@@ -5,7 +5,14 @@ counter=0
 
 # Read the prompt template from prompt_template.txt
 prompt_template=$(cat prompt_template.txt)
-   
+
+# Get the total number of lines in the input file (excluding the header)
+if [[ -f "${1:-/dev/stdin}" ]]; then
+    total_lines=$(wc -l < "${1:-/dev/stdin}")
+else
+    total_lines=0
+fi
+
 # Function to make a call to the local LLM and parse the response
 api_call() {
     local club_name="$1"
@@ -27,6 +34,11 @@ api_call() {
     echo "$response" >> master_output.jsonl
 }
 
+# Clear the master output files
+> master_output.jsonl
+> master_output.json
+> master_output.csv
+
 # Read input from a file or stdin
 while IFS= read -r line || [[ -n "$line" ]]; do
     # Skip the first line (header)
@@ -41,9 +53,11 @@ while IFS= read -r line || [[ -n "$line" ]]; do
 done < "${1:-/dev/stdin}"
 
 # Create a valid JSON array from the JSONL file
-echo "[" > master_output.json
-sed "$!s/$/,/" master_output.jsonl >> master_output.json
-echo "]" >> master_output.json
+#echo "[" > master_output.json
+#sed "$!s/$/,/" master_output.jsonl >> master_output.json
+#echo "]" >> master_output.json
+# Create a valid JSON array from the JSONL file
+jq --slurp '.' master_output.jsonl > master_output.json
 
 # Convert JSON to CSV using jq
 jq -r '["club_name", "end_of_spell", "country", "division", "full_name", "country_confidence", "division_confidence", "full_name_confidence"], (.[] | [.club_name, .end_of_spell, .country, .division, .full_name, .country_confidence, .division_confidence, .full_name_confidence]) | @csv' master_output.json > master_output.csv

### 2024-05-15 LLM-work/post_process.sh
Create post_process.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+# Post-processing script
+# This script takes the master_output.jsonl file as input
+# and generates a cleaned master_output_cleaned.jsonl file
+# containing only the JSON part of the responses.
+# It also converts the cleaned JSON data to a CSV file.
+
+# Check if the input file is provided
+if [ -z "$1" ]; then
+    echo "Usage: $0 <master_output.jsonl>"
+    exit 1
+fi
+
+input_file="$1"
+cleaned_jsonl_file="master_output_cleaned.jsonl"
+json_file="master_output.json"
+csv_file="master_output.csv"
+
+# Clear the output files
+> "$cleaned_jsonl_file"
+> "$json_file"
+> "$csv_file"
+
+# Process each line of the input file
+while IFS= read -r line; do
+    # Extract the JSON part from the line
+    json_part=$(echo "$line" | sed -n '/^{/,/^}$/p' | jq -c '.')
+
+    # Write the JSON part to the cleaned output file
+    echo "$json_part" >> "$cleaned_jsonl_file"
+done < "$input_file"
+
+# Create a valid JSON array from the cleaned JSONL file
+jq --slurp '.' "$cleaned_jsonl_file" > "$json_file"
+
+# Convert JSON to CSV
+jq -r '[["club_name", "end_of_spell", "spell_type", "country", "tier", "country_probability", "tier_probability"]] + (.[].response.variables[] | [.value, .value]) + (.[].response.results[] | [.value, .value, .value, .value, .value])' "$json_file" > "$csv_file"
+
+echo "Post-processing completed."
+echo "Cleaned output written to $cleaned_jsonl_file"
+echo "JSON output written to $json_file"
+echo "CSV output written to $csv_file"

### 2024-05-15 LLM-work/LLM_data_generator.sh
updates for new llama3 template

@@ -6,38 +6,29 @@ counter=0
 # Read the prompt template from prompt_template.txt
 prompt_template=$(cat prompt_template.txt)
 
-# Get the total number of lines in the input file (excluding the header)
-if [[ -f "${1:-/dev/stdin}" ]]; then
-    total_lines=$(wc -l < "${1:-/dev/stdin}")
-else
-    total_lines=0
-fi
-
 # Function to make a call to the local LLM and parse the response
 api_call() {
     local club_name="$1"
     local end_of_spell="$2"
-    local temp_output="temp_response.txt"
+    local temp_output="temp_response.txt" # Temporary file to store LLM response
 
     # Replace placeholders in the prompt template with local variables
     local prompt=$(echo "$prompt_template" | sed "s/<club_name>/${club_name}/g; s/<end_of_spell>/${end_of_spell}/g")
 
     # Call the local LLM model
-    echo "$prompt" | ollama run llama3 > "$temp_output"
+    echo "$prompt" | ollama run llama3:70b > "$temp_output"
     local response=$(cat "$temp_output")
+
+    # Extract the JSON part from the response
+    local json_response=$(echo "$response" | sed -n '/<|start_header_id|>assistant<|end_header_id|>/,/<|eot_id|>/p' | sed 's/<|start_header_id|>assistant<|end_header_id|>//' | sed 's/<|eot_id|>//')
 
     # Increment counter
     ((counter++))
     echo "Processing club ${club_name} (${end_of_spell}) - ${counter} of ${total_lines} processed"
 
-    # Append the JSON response to the master output file
-    echo "$response" >> master_output.jsonl
+    # Write the JSON response to the master output file
+    echo "$json_response" >> master_output.jsonl
 }
-
-# Clear the master output files
-> master_output.jsonl
-> master_output.json
-> master_output.csv
 
 # Read input from a file or stdin
 while IFS= read -r line || [[ -n "$line" ]]; do
@@ -53,11 +44,7 @@ while IFS= read -r line || [[ -n "$line" ]]; do
 done < "${1:-/dev/stdin}"
 
 # Create a valid JSON array from the JSONL file
-#echo "[" > master_output.json
-#sed "$!s/$/,/" master_output.jsonl >> master_output.json
-#echo "]" >> master_output.json
-# Create a valid JSON array from the JSONL file
 jq --slurp '.' master_output.jsonl > master_output.json
 
-# Convert JSON to CSV using jq
[…]

### 2024-05-15 LLM-work/LLM_data_generator.sh
Update LLM_data_generator.sh

@@ -5,7 +5,12 @@ counter=0
 
 # Read the prompt template from prompt_template.txt
 prompt_template=$(cat prompt_template.txt)
-
+# Get the total number of lines in the input file (excluding the header)
+if [[ -f "${1:-/dev/stdin}" ]]; then
+    total_lines=$(wc -l < "${1:-/dev/stdin}")
+else
+    total_lines=0
+fi
 # Function to make a call to the local LLM and parse the response
 api_call() {
     local club_name="$1"

### 2024-06-04 paper.qmd
updates to the main paper

@@
 
-**CEO Turnover and Firm Performance**
+Here is the updated literature review with the corporate CEO turnover papers included in the summary table:
 
-A robust body of research demonstrates a negative correlation between poor organizational performance and involuntary CEO dismissal (@defond1999effect).
-Both stock returns and accounting metrics indicate that failing to achieve performance benchmarks raises turnover probability, though the magnitude of effects prove statistically significant yet substantively minimal across analyses [@gibbons1990relative; @farrell2003impact].
+Managerial turnover in professional association football (soccer) has been a subject of significant interest among researchers in sports economics and management, drawing parallels with the corporate world.
+The high-stakes nature of the sport, coupled with the intense pressure to perform, has led to a high rate of managerial dismissals and voluntary departures, similar to the dynamics observed in CEO turnover and firm performance.
+This literature review synthesises the existing research on the determinants and consequences of managerial turnover in professional football, incorporating insights from the corporate context.
 
-Building on seminal insights by @march1958organizations and @cyert1963behavioral, subsequent scholarship illuminates how boards of directors explore solutions and prompt managerial changes when results underperform expectations.
-Managers able to realise forecasted outputs appear less susceptible to replacement than those unable to reach projected thresholds, irrespective of analogous absolute performance [@bandura1991self; @haleblian2006cognitive].
-Boards frequently assess leaders against firm-specific expectations, benchmarking actual versus anticipated outcomes and attributing divergence to the CEO [@greve1998performance; @defond1999effect; @wiersema2011ceo].
-As proxies for performance expectations, earnings forecasts strongly predict turnover likelihood, though also capture managerial efforts toward systematic issue management [@ieper2014performance]
+Numerous studies have investigated the relationship between organisational performance and managerial turnover in football, mirroring the negative correlation between poor organizational performance and involuntary CEO dismissal \cite{defond1999effect}.
+Audas, Dobson, and Goddard \cite{audas2000organizational} analysed managerial job-termination hazard functions in English professional soccer from 1972 to 1997, covering 2,365 managerial spells, and found that short-term fluctuations in performance strongly influence the involuntary termination hazard, which is also heavily dependent on the team's current league position relative to its position when the manager took charge and the win ratio over the entire spell.
+The same authors \cite{audas2000team} also investigated the relationship between team performance and managerial change in the English Football League between 1972 and 1993, examining 1,531 managerial spells, revealing that poor recent form drives many managerial terminations, whilst managerial turnover is more rapid in the lower divisions.
 
-**Strategic Expectations Management**
+Performance expectations play a significant role in managerial dismissals, both in the corporate world and in professional football.
+Boards of directors in the corporate world assess leaders against firm-specific expectations, benchmarking actual versus anticipated outcomes and attributing divergence to the CEO \cite{greve1998performance,defond1999effect,wiersema2011ceo}.
+Similarly, football clubs evaluate managers based on their ability to meet performance expectations.
+Allen et al.
+\cite{allen2012performance} investigated this question theoretically and empirically in the context of the National Football League (NFL), analyzing 477 coach-year observations from 1978 to 2005, finding that the probability of coach dismissal increased in the post-salary cap era and that concrete measures of an organisation's player talent, coaching talent, and on-field performance gained importance as determinants of turnover, indicative of increased expectations.
+Pieper, Nüesch, and Franck \cite{pieper2014performance} examined 2,680 coach-game observations from the German Bundesliga between 1993 and 2010, showing that a one-standard-deviation increase in performance expectations nearly doubles the coach's dismissal probability, controlling for team performance and unobserved team heterogeneity.
 
-Endogeneity concerns thus emerge, as information asymmetries afford CEOs latitude to strategically time media announcements and influence external stakeholder interpretations [@westphal2010matter; @westphal2011avoiding].
-Similarly, football managers degrade expectations through injury pronouncements and other excuses that deflect responsibility.
-Evidence remains limited regarding precise managerial tactics shaping performance benchmarks [@pieper2014performance].
-Some research proposes that higher expectations decrease capital costs and increase share prices [@francis1997relative], while other studies indicate systematic “expectation management” wherein CEOs restrict forecast escalation [@bartov2002rewards; @goyal2002board].
-This restraint purportedly reduces involuntary turnover incidence.
+The concept of strategic expectations management, wherein CEOs influence external stakeholder interpretations and shape performance benchmarks \cite{westphal2010matter,westphal2011avoiding}, can also be applied to football managers.
+Managers may use tactics such as injury pronouncements and other excuses to deflect responsibility and manage expectations.
+However, evidence remains limited regarding the precise managerial tactics used in this context \cite{pieper2014performance}.
 
-The majority of empirical literature upholds poor performance as the primary antecedent of managerial replacement [@groves1995china; @hudson2004managerial].
-Though post-succession improvements appear frequently observed, findings regarding causal impacts on organizational outcomes remain mixed [@cools2003value].
-Difficulties persist in identifying relevant temporal lags and indicators within corporate performance-turnover analyses.
+Social media pressure and coach characteristics have also been identified as factors influencing managerial turnover.
+Attie et al.
+\cite{attie2023getting} proposed machine learning models to characterise the determinants of managerial dismissals, utilizing data from the English Premier League, finding that social media pressure from fans on Twitter is associated with managerial sacking, alongside traditional football statistics.
+Semmelroth et al.
+\cite{semmelroth2021time} investigated the determinants of voluntary and involuntary head coach turnovers in Major League Soccer (MLS) from 2004 to 2019, analyzing 6,584 coach-game observations, revealing that coach reputation decreases dismissal probabilities, whilst coach age increases quit rates.
+Additionally, Bell, Brooks, and Markham \cite{bell2013performance} investigated the sacking of managers in the English Premier League from 1992 to 2012, examining 60 managerial dismissals, finding that a higher total wage bill, a lower win percentage, and a lower position in the league table all increase the probability of a manager being sacked.
 
-**Parallels in Sport**
+The consequences of managerial turnover on team performance have been a subject of debate in the literature.
+Audas, Dobson, and Goddard \cite{audas2000team} found that managerial change appears to have a harmful effect on team performance immediately following a managerial termination in the English Football League.
+Tena and Forrest \cite{tena2007within} examined the consequences of within-season dismissals of managers in the top division of the Spanish Football League from 2002 to 2005, covering 132 managerial changes, demonstrating that an improvement in results tended to be achieved but only in home matches, suggesting that appeasing fans can have on-the-field benefits.
+However, Van Ours and van Tuijl \cite{van2015season} studied the causes and consequences of in-season changes of head coaches in Dutch professional football, analyzing 578 managerial spells between 1986 and 2004, and concluded that the replacement of head coaches does not improve team performance, as the performance of a control group of coach replacements that did not occur also improved.
+Similarly, Flores, Forrest, and Tena \cite{flores2012decision} investigated football manager dismissals in Argentina, examining 1,995 matches from 2005 to 2008, and detected a tendency for a change of manager to be followed by deterioration in team performance, consistent with decisions being driven by fan and media pressure rather than a realistic hope of improving the club's position.
+Bruinshoofd and ter Weel \cite{bruinshoofd2003manager} also examined the effectiveness of manager dismissals in Dutch football, covering 12 seasons from 1988 to 2000, and suggested that sacking a manager is neither effective nor efficient in terms of improving team performance.
 
-In drawing parallels with corporate leadership, football managers constitute integral strategic and operational decision-makers whose choices shape competitiveness and results [@pieper2014performance].
-While factors like injuries constrain agency, negative performance often escalates dismissal odds given close linkages between the managerial role and team outputs [@hoffler2003new].
-Contemporary scholarship utilizing bookmaker odds reveals that failure to achieve expected sporting outcomes precipitates coaching turnover [@pieper2014performance; @vanours2016inseason; @bruinshoofd2003manager].
+Several studies have investigated the factors influencing managerial survival in football.
+Barros, Frick, and Passos \cite{barros2009coaching} analysed how long head coaches survive in the clubs of the German Bundesliga, covering 398 managerial spells from 1981 to 2003, finding that head coaches of successful teams and those working during the more recent 'Bosman Effect' period are more likely to survive, whilst head coaches of clubs with relatively high team wage bills are likely to survive for shorter periods.
+D'Addona and Kind \cite{daddona2014forced} conducted an empirical analysis of manager turnover in the four major English leagues from 1949 to 2008, examining 2,376 managerial changes, revealing that both the absolute frequency and the sensitivity of firing decisions on the outcome of recent matches steadily and significantly increased during the six decades covered by the sample, reflecting the increased level of competition and economic importance of the English soccer leagues.
 
-In a rare longitudinal approach, @bachan2005hazard model seasonal hazard rates, determining league position overrides individual attributes in predicting managerial survival.
-Yet other analyses of match outcomes bypass control group issues while accounting for difficulty variances.
-@koning2003econometric and @forrest2000behaviour find sporadic evidence that replacement temporarily boosts performance.
-But several studies propose frequent “scapegoating” wherein termination aims to appease stakeholders rather than improve competition, with managerial change reliably hampering short-term results [@koning2003econometric; @dobson2011economics; @audas2002impact].
+Bachan, Reilly, and Witt \cite{bachan2005hazard} employed a longitudinal approach in modeling seasonal hazard rates and determining the importance of league position in predicting managerial survival, utilizing data from the English Football League covering three seasons from 2001 to 2004.
+Their findings emphasize the significance of team performance in shaping managerial turnover decisions.
+Additionally, the work of Koning \cite{koning2003econometric}, Forrest and Simmons \cite{forrest2000behaviour}, and others regarding the short-term impact of managerial change on team performance highlights the complex dynamics of post-turnover outcomes.
 
-@tena2007within importantly highlight financial relegation risks and failing historical powers as motivational factors.
-While the former escalates turnover incidence, the latter proves insignificant as inferior clubs primarily dismissed coaches.
-Ultimately, teams appear to utilize termination following perceived underperformance relative to expectations shaped by factors like salary budgets.
+Tena and Forrest \cite{tena2007within} provide valuable insights into the role of financial relegation risks and failing historical powers as motivational factors for managerial turnover.
+Their findings suggest that the threat of relegation escalates turnover incidence, while the performance of historically successful clubs proves less significant in driving dismissal decisions.
+
+Further research has delved into the effectiveness of in-season coach changes and the impact of managerial turnover on player performance.
+Besters, van Ours, and van Tuijl \cite{besters2016effectiveness} studied the effectiveness of in-season coach changes in Dutch football, examining 18 seasons from 1986 to 2004, considering the heterogeneity of coach ability and suggesting that coach ability is an important factor in determining team performance.
+Muehlheusser, Schneemann, and Sliwka \cite{muehlheusser2016impact} analysed the impact of managerial turnover on player performance in German football, utilizing data from the German Bundesliga covering six seasons from 2007 to 2013, showing that a coach dismissal is typically followed by an increase in the number of yellow and red cards, indicating that players exert more effort under the new coach, possibly to impress and secure their position in the team.
+
+In conclusion, the literature on managerial turnover in professional association football highlights the complex interplay of factors that influence dismissals and voluntary departures, including organisational and team performance, performance expectations, social media pressure, and coach characteristics.
+The consequences of managerial change on team performance remain a subject of debate, with some studies suggesting short-term improvements and others indicating no significant effect or even deterioration in performance.
+The parallels drawn between the corporate world and professional football provide valuable insights into the dynamics of managerial turnover and its determinants.
+Further research could explore the long-term consequences of managerial turnover, the impact of managerial change on player motivation and performance, and the role of media scrutiny and fan sentiment in driving dismissal decisions.
+As the football industry continues to evolve, with increasing financial stakes and global attention, understanding the dynamics of managerial turnover will remain a critical area of inquiry for sports economists and management researchers.
+
+Summary Table of References
+| Authors                             | Year | Journal                                     | Country     | Focus                                                                                              |
+|-------------------------------------|------|---------------------------------------------|-------------|---------------------------------------------------------------------------------------------------- |
+| DeFond & Park                       | 1999 | The Accounting Review                       | USA         | Poor organizational performance and involuntary CEO dismissal                                      |
+| Greve                               | 1998 | Strategic Management Journal                | USA         | Firm performance and CEO turnover                                                                  |
+| Wiersema & Zhang                    | 2011 | Strategic Management Journal                | USA         | CEO dismissal and firm-specific performance expectations                                           |
+| Westphal & Deephouse                | 2010 | Administrative Science Quarterly            | USA         | CEO influence on external stakeholder interpretations                                              |
+| Westphal & Zajac                    | 2011 | Administrative Science Quarterly            | USA         | CEO influence on external stakeholder interpretations                                              |
+| Audas, Dobson, & Goddard            | 2000 | Managerial and Decision Economics           | England     | Organisational performance and managerial turnover                                                 |
+| Audas, Dobson, & Goddard            | 2000 | Economic Affairs                            | England     | Team performance and managerial change                                                             |
+| Frick, Barros, & Prinz              | 2010 | European Journal of Operational Research    | Germany     | Head coach dismissals in the German Bundesliga                                                     |
+| Allen, Panian, & Lotz               | 2012 | Journal of Sports Economics                 | USA         | Performance expectations and managerial dismissal in the NFL                                       |
+| Attie, West, McDermott, & Luque     | 2023 | Complex Networks XIV                        | England     | Predicting managerial dismissals using social media pressure                                       |
+| Semmelroth, Deutscher, & Orlowski    | 2021 | Journal of Sports Economics                 | USA         | Coach dismissals and quits in Major League Soccer                                                  |
+| Van Ours & van Tuijl                | 2015 | Economic Inquiry                            | Netherlands | In-season head coach dismissals and team performance                                               |
+| Tena & Forrest                      | 2007 | European Journal of Operational Research    | Spain       | Within-season dismissal of football coaches                                                        |
+| Bachan, Reilly, & Witt              | 2008 | Journal of the Operational Research Society | England     | Hazard of being an English football league manager                                                 |
+| Barros, Frick, & Passos             | 2009 | Applied Economics                           | Germany     | Coaching survival in the German Bundesliga                                                         |
+| d'Addona & Kind                     | 2014 | Journal of Sports Economics                 | England     | Long-term perspective on forced manager turnover                                                   |
+| Pieper, Nüesch, & Franck            | 2014 | Schmalenbach Business Review                | Germany     | Performance expectations and managerial replacement decisions                                      |
+| Flores, Forrest, & Tena             | 2012 | European Journal of Operational Research    | Argentina   | Football manager dismissals and consequences in Argentina                                          |
+| Bruinshoofd & ter Weel              | 2003 | European Journal of Operational Research    | Netherlands | Manager dismissals and performance dips in Dutch football                                          |
+| Holmes, Nowell, & Scelles           | 2010 | Journal of Sports Economics                 | USA         | College football coach dismissals                                                                  |
+| Bell, Brooks, & Markham             | 2013 | Economics & Finance Research                | England     | Managerial sacking in the English Premier League                                                   |
+| Besters, van Ours, & van Tuijl      | 2016 | De Economist                                | Netherlands | Effectiveness of in-season manager changes considering coach ability                               |
+| Muehlheusser, Schneemann, & Sliwka | 2016 | Economic Inquiry                            | Germany     | Impact of managerial change on player performance                                                  |
+: Summary of literature
 

### 2024-06-04 LLM-work/LLM_data_generator.sh

@@ -4,7 +4,19 @@
 counter=0
 
 # Read the prompt template from prompt_template.txt
-prompt_template=$(cat prompt_template.txt)
+prompt_template=$(cat prompts/llama3_prompt.txt)
+
+# Clear the master output files
+> master_output_test.jsonl
+> master_output_test.json
+
+
+# Get the total number of lines in the input file (excluding the header)
+if [[ -f "${1:-/dev/stdin}" ]]; then
+    total_lines=$(wc -l < "${1:-/dev/stdin}")
+else
+    total_lines=0
+fi
 
 # Function to make a call to the local LLM and parse the response
 api_call() {
@@ -16,18 +28,19 @@ api_call() {
     local prompt=$(echo "$prompt_template" | sed "s/<club_name>/${club_name}/g; s/<end_of_spell>/${end_of_spell}/g")
 
     # Call the local LLM model
-    echo "$prompt" | ollama run llama3:70b > "$temp_output"
+    echo "$prompt" | ollama run llama3 > "$temp_output"
     local response=$(cat "$temp_output")
 
     # Extract the JSON part from the response
-    local json_response=$(echo "$response" | sed -n '/<|start_header_id|>assistant<|end_header_id|>/,/<|eot_id|>/p' | sed 's/<|start_header_id|>assistant<|end_header_id|>//' | sed 's/<|eot_id|>//')
+#   local json_response=$(echo "$response" | sed -n '/<|start_header_id|>assistant<|end_header_id|>/,/<|eot_id|>/p' | sed 's/<|start_header_id|>assistant<|end_header_id|>//' | sed 's/<|eot_id|>//')
 
     # Increment counter
     ((counter++))
     echo "Processing club ${club_name} (${end_of_spell}) - ${counter} of ${total_lines} processed"
-
+    echo "$prompt"
     # Write the JSON response to the master output file
-    echo "$json_response" >> master_output.jsonl
+#    echo "$json_response" >> master_output.jsonl
+     echo "$response" >> master_output_test.jsonl
 }
 
 # Read input from a file or stdin
@@ -44,7 +57,7 @@ while IFS= read -r line || [[ -n "$line" ]]; do
 done < "${1:-/dev/stdin}"
 
 # Create a valid JSON array from the JSONL file
-jq --slurp '.' master_output.jsonl > master_output.json
+#jq --slurp '.' master_output_test.jsonl > master_output.json
 
 # Convert JSON to CSV
[…]

### 2024-06-04 LLM-work/adjust_text.py

@@ -1,23 +1,0 @@
-import pandas as pd
-import re
-file_path = 'LLM-work/output_adj.csv'
-df = pd.read_csv(file_path)
-df['API.Response'] = df['API.Response'].astype(str)
-# Inspect the column types
-print(df.dtypes)
-print(df['API.Response'].head())
-# Define a function to remove everything before the first instance of "Question"
-def remove_before_question(text):
-    index = text.find("Question 1")
-    if index != -1:  # If "Question" is found
-        return text[index:]
-    else:
-        return text  # If "Question" is not found, return the original text
-# Apply the function to the 'text' column to remove everything before the first instance of "Question"
-# convery API.Response to string
-df['text'] = df['API.Response'].apply(remove_before_question)
-df.drop(columns=['API.Response'], inplace=True)
-print(df.head())
-df.to_csv('LLM-work/output_adj.csv', index=False)
-
-

### 2024-06-04 LLM-work/csv_hack.r

@@ -1,5 +1,0 @@
-data1 <- read.csv("LLM-work/output1.csv")
-#write.csv(data, "LLM-work/output1adj.csv", row.names = FALSE)
-data2 <- read.csv("LLM-work/output2.csv")
-data2 <- data2[,-1]
-write.csv(rbind(data1,data2), "LLM-work/output_adj.csv", row.names = FALSE)

### 2024-06-04 LLM-work/extract_answers.py

@@ -1,33 +1,0 @@
-import pandas as pd
-import re
-file_path = 'LLM-work/output_adj.csv'
-df = pd.read_csv(file_path)
-df['text'] = df['text'].astype(str)
-# Define a function to extract the text after each instance of "Answer" but before each instance of "confidence" along with confidence score
-def extract_answers(text):
-    answers = re.findall(r'Answer(?:\s*\d+)?: (.*?) (?:confidence rating|confidence level|confidence)?:? (\d+)', text, re.IGNORECASE)
-    return answers    
-
-# Define a function to split the answers into separate columns
-def split_answers(answers):
-    answer_dict = {'Answer_' + str(i+1): answer[0] for i, answer in enumerate(answers)}
-    answer_dict['LLM_assigned_confidence_1'] = answers[0][1] if answers else None
-    answer_dict['LLM_assigned_confidence_2'] = answers[1][1] if len(answers) > 1 else None
-    answer_dict['LLM_assigned_confidence_3'] = answers[2][1] if len(answers) > 2 else None
-    return pd.Series(answer_dict)
-
-# Apply the function to the 'text' column to extract the text after each instance of "Answer" but before each instance of "confidence"
-# remove any brackets from the text before extracting answers
-df['text'] = df['text'].apply(lambda x: x.replace('(', '').replace(')', '').replace('[', '').replace(']', ''))
-df['answers'] = df['text'].apply(extract_answers)
-#if df['answers'].empty:
-#    df['answers'] = df['text'].apply(lambda x: re.findall(r'Answer:\s*(.*?)\s*\((?:Confidence(?:\s*level)?:)?\s*(\d+)\)',x) if x else None)
-# Split the answers into separate columns
-df[['Answer_1', 'Answer_2', 'Answer_3', 'LLM_assigned_confidence_1', 'LLM_assigned_confidence_2', 'LLM_assigned_confidence_3']] = df['answers'].apply(split_answers)
-
-# Print the full text of these rows with empty 'Answer_1' column
-print(df[df['Answer_1'].isnull()]['text'])
-# Drop the 'answers', 'text', 'API.response' columns as they are no longer needed
-#df.drop(columns=['text'], inplace=True)
-df.drop(columns=['answers'], inplace=True)
-df.to_csv('LLM-work/outputadj_parsed.csv', index=False)

### 2024-06-04 LLM-work/json_objs_extract.py

@@ -1,0 +1,15 @@
+import json
+
+# Open the input and output files
+with open('master_output.jsonl', 'r') as infile, open('output.jsonl', 'w') as outfile:
+    json_object = ''
+    for line in infile:
+        json_object += line.strip()
+        if line.strip().endswith('}'):
+            # Parse the JSON object and re-serialize it into a single-line format
+            data = json.loads(json_object)
+            json_singleline = json.dumps(data, separators=(',', ':'))
+            # Write the single-line JSON object to the output file
+            outfile.write(json_singleline + '\n')
+            # Reset the JSON object
+            json_object = ''

### 2024-06-04 LLM-work/loop_w_counter.sh

@@ -1,55 +1,0 @@
-#!/bin/bash
-
-# Counter
-counter=0
-
-# Function to make a call to the local LLM and parse the response
-api_call() {
-  local club_name="$1"
-  local end_of_spell="$2" # Assuming this variable is provided
-  local temp_output="temp_response.txt" # Temporary file to store LLM response
-  
-  # Concatenate all questions into a single prompt
-  local prompt="""
-  You are to search for information about ${club_name} on ${end_of_spell}. 
-  Then answer the following questions filling in the blanks with the correct information.
-  Only provide one word answers.
-  Rate your confidence for each answer answer from 1 to 10.
-  Question 1: In which country does ${club_name} play?
-  Answer1: _________ confidence: _________
-  Question 2: On ${end_of_spell}, what division was ${club_name} in? 
-  Answer2: _________ confidence: _________
-  Question 3: What is the full name of ${club_name}?
-  Answer3: _________ confidence: _________
-  """
-  
-  # Call the local LLM model
-  echo "$prompt" | ollama run llama3 > "$temp_output"
-  local response=$(cat "$temp_output")
-  
-  # Increment counter
-  ((counter++))
-  
-  echo "Processing club ${club_name} (${end_of_spell}}) - ${counter} of ${total_lines} processed"
-  
-  # Assuming the response can be directly appended. Adjust based on the actual output format
-  echo "${counter},${club_name},${end_of_spell},\"${response}\"" >> "${output_file}"
-  
-  # Cleanup temporary file
-  rm -f "$temp_output"
-}
-
-input_file="LLM-work/input2.csv"
-output_file="LLM-work/output2.csv"
-echo "Counter,club_name,end_of_spell,API Response" > "${output_file}"
-
-# Calculate total lines in the input file
-total_lines=$(wc -l < "${input_file}")
-
-while IFS=',' read -r club_name end_of_spell; do
-  if [[ -n "$club_name" && -n "$end_of_spell" ]]; then
-    api_call "$club_name" "$end_of_spell"
-  fi
-done < "${input_file}"
-
-echo "Done processing all clubs. Total responses processed: $(( $(wc -l < "${output_file}") - 1 ))"

### 2024-06-04 LLM-work/process_json.py

@@ -1,0 +1,44 @@
+import pandas as pd
+import json
+
+def preprocess_data(raw_data):
+    data = []
+    current_entry = ""
+
+    for line in raw_data.splitlines():
+        line = line.strip()
+        if line:
+            # Accumulate lines until we find a closing brace
+            current_entry += line
+            if line.endswith("}"):
+                try:
+                    entry = json.loads(current_entry)
+
+                    # # Standardize date format (assuming DD/MM/YY)
+                    # if "/" in entry['date']:
+                    #     day, month, year = entry['date'].split("/")
+                    #     entry['date'] = f"20{year}-{month}-{day}"
+
+                    data.append(entry)
+                except json.JSONDecodeError as e:
+                    print(f"Warning: Skipping invalid JSON object: {current_entry} - Error: {e}")
+                finally:
+                    current_entry = ""  # Reset for the next entry
+
+    df = pd.DataFrame(data)
+    return df
+
+# Raw data from the JSON file named master_output.jsonl
+with open("master_output.jsonl") as f:
+    raw_data = f.read()
+
+# Preprocess the data
+df = preprocess_data(raw_data)
+
+# Reorder columns
+df = df[['club', 'date', 'country', 'League', 'Tier']]
+
+# Write to CSV
+df.to_csv("cleaned_football_data.csv", index=False)
+
+print(f"Processed {len(df)} entries and saved to cleaned_football_data.csv")

### 2024-06-05 paper.qmd
updates to LLM work and paper_new.qmd · 92884aab - Gogs

@@
 ```{r}
-
-```
-
-```{r}
 #|label: tbl-managertype
@@
 plotly::ggplotly(spell_count)
-```
-
-```{r}
-
-```
-
-```{python}
-import pandas as pd
-import time
-from transformers import pipeline
-
-generator = pipeline("text-generation")
-
-# Load the unique club names from the CSV file
-spells1 = pd.read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
-club_names=spells1['club'].unique()
-
-# Initialize an empty list to store the results
-results = []
-
-# Iterate over the array of club names and add a timer for each iteration
-start_time = time.time()
-for club in club_names:
-    # Prepare the prompt for the model
-    prompt = f"Provide information about the soccer club {club}: its country of origin,  division level, and whether it is a first  team or a youth team."
-
-    # Generate the response using the model
-    start = time.time()
-    responses=generator(prompt)
-
-    # Assuming the first (or only) response is what we're interested in
-    response_text = responses[0]
-
-    # Store the response, elapsed time for this iteration and total elapsed time in our results list
-    results.append({'ClubName': club, 'Information': response_text, 'ElapsedTimePerIteration': time.time() - start, 
-'TotalElapsedTime': time.time() - start_time})
-
-# Convert the results list to a DataFrame
-import pandas as pd
-results_df = pd.DataFrame(results)
-
-# Display the DataFrame to verify the results
-print(results_df)
-
-# Specify the file path for the CSV file
-csv_file_path = 'soccer_clubs_information_hf.csv'
-
-# Save the DataFrame to a CSV file
-results_df.to_csv(csv_file_path, index=False)
-
-print(f"Results have been saved to {csv_file_path}")
-
 ```

### 2024-06-05 paper_new.qmd
updates to LLM work and paper_new.qmd · 92884aab - Gogs

--- 2024-04-10 paper_new.qmd
@@
 format:
-    pdf:
+  pdf: default
+  elsevier-pdf:
+    keep-tex: true    
     fig-pos: "H"
@@
   theme_minimal() -> spell_count
-plotly::ggplotly(spell_count)
-```
-
-```{r}
-library(clipr)
-unique(spells$Country) |> write_clip()
-```
-
-```{r}
-# Assuming the LLM output is stored in a variable called 'llm_output'
-categories <- unique(spells$Country)
-
-# Remove leading/trailing whitespace and convert to lowercase
-categories <- trimws(categories)
-categories <- tolower(categories)
-
-# Remove any leading/trailing punctuation marks
-categories <- gsub("^[[:punct:]]+|[[:punct:]]+$", "", categories)
-
-# Replace ' - ' and ' . ' with '.'
-categories <- gsub(" - | \\. ", ".", categories)
-
-# Replace 'not applicable', 'none', 'unknown', 'not found', 'not available', 'n/a' with NA
-categories[categories %in% c("not applicable", "none", "unknown", "not found", "not available", "n/a","","0")] <- NA
-
-# Categorize responses indicating LLM cannot find answer
-llm_cannot_answer <- grepl("^i am not|^i cannot|^i don't|^i am just an ai|^i'm just an ai", categories)
-categories[llm_cannot_answer] <- "LLM cannot find answer"
-
-# Remove rows with NA values
-categories <- categories[!is.na(categories)]
-
-# Remove duplicate categories
-categories <- unique(categories)
-
-# Sort the categories alphabetically
-categories <- sort(categories)
-categories <- trimws(categories)
-# Print the cleaned categories
-unique(categories) |> write_clip()
-```
-
-```{r}
-library(countries)
-list_countries() |> length()
-```
-
-```{r}
-# Assuming the list is stored in a variable called 'categories'
-countries <- gsub("^.*\\b(\\w+)\\.*$", "\\1", spells$Country, perl = TRUE)
-
-# Replace common non-country phrases with NA
-non_countries <- c("based on my training data", "based on training data", "LLM cannot find answer", "none", "not applicable", "not found in my training data", "not sure", 
-                   "unknown", "soccer", "tennis", "world cup", "football soccer", "northern", 
-                   "rome", "soccer football", "west africa", "south america", "central america", 
-                   "eastern europe", "north macedonia", "fifa", "uefa", "asia", "eu", "uefa european football association","uefa european", "eurozone", "caribbean", "cricket", "\\bi'm.*", "\\bi have.*", "\\bi cannot.*",
-                   "\\bi don't.*", "\\bi couldn't.*", "\\bna\\b", "\\bn/a\\b", "i can","\\bi am not aware","i am", "answer:", "africa", "europe", 
-                   "middle east", "east germany", "soviet union", "uae", "uk", "usa", "world")
-countries[countries %in% non_countries] <- NA
-
-# Remove any leading/trailing whitespace
-countries <- trimws(countries)
-
-# Replace empty strings with NA
-countries[countries == ""] <- NA
-
-# Merge similar country names
-# Create a named vector for country name mappings
-country_mappings <- c(
-  "_England_" = "England",
-  "_Belgium_" = "Belgium",
-  "_Germany_" = "Germany",
-  "_Italy_" = "Italy",
-  "_Serbia_" = "Serbia",
-  "England -" = "England",
-  "States" = "United States",
-  "United States -" = "United States",
-  "Kingdom" = "United Kingdom",
-  "United Kingdom UK -" = "United Kingdom",
-  "Democratic Republic of Congo" = "Democratic Republic of the Congo",
-  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
-  "Soviet Union" = "Russia",
-  "Soviet Union former" = "Russia",
-  "Soviet Union formerly" = "Russia",
-  "Russia formerly Soviet Union" = "Russia",
-  "Yugoslavia" = "Serbia",
-  "Yugoslavia now Serbia" = "Serbia",
-  "Yugoslavia or SFR Yugoslavia" = "Serbia",
-  "Serbia formerly Yugoslavia" = "Serbia",
-  "East Germany" = "Germany",
-  "East Germany GDR" = "Germany",
-  "East Germany Germany" = "Germany",
-  "East Germany Germany Democratic Republic" = "Germany",
-  "Macedonia" = "North Macedonia",
-  "Macedonia formerly known as the Republic of Macedonia" = "North Macedonia",
-  "Burma" = "Myanmar",
-  "Myanmar Burma" = "Myanmar",
-  "Congo" = "Democratic Republic of the Congo",
-  "Democratic Republic of Congo DRC" = "Democratic Republic of the Congo",
-  "Ivoire" = "Ivory Coast",
-  "Holland" = "Netherlands",
-  "Holland Netherlands" = "Netherlands",
-  "United Arab Emirates UAE" = "United Arab Emirates",
-  "UAE United Arab Emirates" = "United Arab Emirates",
-  "United Kingdom UK" = "United Kingdom",
-  "UK" = "United Kingdom",
-  "ANDORA" = "Andorra",
-  "Faso" = "Burkina Faso",
-  "Rica" = "Costa Rica",
-  "Salvador" = "El Salvador"
-)
-
-# Merge similar country names using the country_mappings vector
-for (i in seq_along(countries)) {
-  if (countries[i] %in% names(country_mappings)) {
-    countries[i] <- country_mappings[countries[i]]
-  }
-}
-
-# Handle historical country names
-countries[countries == "Czechoslovakia"] <- NA  # Czechoslovakia no longer exists, split into Czech Republic and Slovakia
-
-# Remove additional non-country values
-non_countries <- c("International", "UEFA", "FIFA", "UEFA European", "European", "AFC", "GDR", "EU", "Eurozone", "UEFA European Football Union")
-countries[countries %in% non_countries] <- NA
-
-# Print the extracted country names
-#countries |> table() |> sort(decreasing = TRUE)
-unique(countries) |> write_clip()
-```
-
-```{r})
-```
-
-```{r}
-table(countries) |> sort(decreasing = TRUE)
+spell_count
 ```
@@
   rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
-         "Cumulative Relative Strength"=b_Standardized_CumRS)
-
-          |>
+         "Cumulative Relative Strength"=b_Standardized_CumRS) |>
   pivot_longer(!.draw &!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
@@
   rename("Points of of Possible"=b_Pct_of_Possible_Points_Won,
-         "Cumulative Relative Strength"=b_Standardized_CumRS)
-  pivot_longer(!.draw&!.iteration&!.chain,names_to = "fixed_effect",values_to = "draws")|>
+         "Cumulative Relative Strength"=b_Standardized_CumRS) |>
+  pivot_longer(!.draw & !.iteration &!.chain,names_to = "fixed_effect",values_to = "draws")|>
   ggplot(aes(y = fixed_effect,
@@
 ggsave(filename = "./plots/logit_baseline.png",width = 12,height = 8)
-
-```
-
-```{r}
-logit |> 
-  ungroup() |>
-  select(cty_factor,.iteration,.chain,conditional_mean_CumRS,conditional_mean_Pcts_of_Possible) |>
-  pivot_longer(!cty_factor&!.iteration&!.chain,names_to = "conditional_mean",values_to = "draws") |>  
-  group_by(cty_factor,conditional_mean) |>
-  mutate(global_mean=mean(draws)) |>
-  ggplot(aes(x = reorder(cty_factor,global_mean),
-             y=draws, 
-             fill =conditional_mean)) +
-  stat_slab() +
-  labs(x="",
-       title="Overall effect on probability of poaching",
-       subtitle="Posterior probability distribution",
-       y="Overall Effect",fill="")  +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-        title = element_text(hjust = 0.5),
-        legend.position = "bottom") +
-  scale_fill_discrete(labels=c("Cumulative Relative Strength","Points out of Possible Points"))
-ggsave(filename = "./plots/logit_by_cty.png",width = 12,height = 8)
 

### 2024-06-05 LLM-work/extract_json.py

@@ -1,0 +1,36 @@
+import json
+
+with open("./LLM-work/responses.txt", 'r') as file:
+  file_content = file.read()
+
+# Find the first and last occurrences of '{' and '}'
+start_index = file_content.find('{')
+end_index = file_content.rfind('}')
+
+# Extract the text between the first '{' and the last '}'
+extracted_text = file_content[start_index:end_index + 1]
+
+# Split the extracted text by newline character
+json_strings = extracted_text.split('\n')
+
+# Remove empty strings
+json_strings = [js for js in json_strings if js.strip()]
+
+# Load the JSON strings into a list of dictionaries
+data = []
+for js in json_strings:
+  try:
+    data.append(json.loads(js))
+  except json.JSONDecodeError as e:
+    print(f"Error decoding JSON string: {js}, Error: {e}")
+
+import pandas as pd
+
+# Create a dataframe from the list of dictionaries
+df = pd.DataFrame(data)
+
+# Display the first 5 rows
+print(df.head().to_markdown(index=False, numalign="left", stralign="left"))
+
+# Print the column names and their data types
+print(df.info())

### 2024-06-05 LLM-work/groq.py

@@ -1,19 +1,0 @@
-import os
-
-from groq import Groq
-
-client = Groq(
-    api_key=os.environ.get("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"),
-)
-
-chat_completion = client.chat.completions.create(
-    messages=[
-        {
-            "role": "user",
-            "content": "Explain the importance of fast language models",
-        }
-    ],
-    model="llama3-8b-8192",
-)
-
-print(chat_completion.choices[0].message.content)

### 2024-06-05 LLM-work/groq.sh

@@ -1,0 +1,2 @@
+export GROQ_API_KEY="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"
+#python your_script.py

### 2024-06-05 scripts/extract_json.R

@@ -1,0 +1,48 @@
+# Install and load the stringr package if not already installed
+# install.packages("stringr")
+library(stringr)
+
+# Read the contents of the txt file
+file_contents <- readLines("./LLM-work/responses.txt")
+
+# Collapse the file contents into a single string
+text <- paste(file_contents, collapse = "\n")
+
+# Extract content within curly brackets using regular expressions
+extracted_content <- str_extract_all(text, "\\{[^{}]*\\}")
+
+# Print the extracted content
+extracted_content |> purrr::flatten() -> extracted_content
+
+library(jsonlite)
+
+# Create a sample list of JSON-like strings
+data_list <- extracted_content
+
+# Function to parse JSON-like strings and handle missing fields
+parse_json_string <- function(json_string) {
+  # Replace single quotes with double quotes
+  json_string <- gsub("'", "\"", json_string)
+  
+  tryCatch(
+    {
+      parsed_data <- fromJSON(json_string)
+      parsed_data$probability <- as.numeric(parsed_data$probability)
+      parsed_data
+    },
+    error = function(e) {
+      warning(paste("Error parsing JSON string:", e$message))
+      return(NULL)
+    }
+  )
+}
+
+# Parse the JSON-like strings and create a data frame
+parsed_data <- lapply(data_list, parse_json_string)
+parsed_data <- do.call(rbind, parsed_data)
+
+# Convert the parsed data to a data frame
+df <- as.data.frame(parsed_data, stringsAsFactors = FALSE)
+
+# Print the resulting data frame
+print(df)

### 2024-06-07 LLM-work/LLM_data_generator.sh
updated with new variables

@@ -1,70 +1,0 @@
-#!/bin/bash
-
-# Counter
-counter=0
-
-# Read the prompt template from prompt_template.txt
-<<<<<<< HEAD
-prompt_template=$(cat prompts/llama3_prompt.txt)
-
-# Clear the master output files
-> master_output_test.jsonl
-> master_output_test.json
-
-
-=======
-prompt_template=$(cat prompt_template.txt)
->>>>>>> 51c97109f287f61e77c97d6ab762010aaff0b428
-# Get the total number of lines in the input file (excluding the header)
-if [[ -f "${1:-/dev/stdin}" ]]; then
-    total_lines=$(wc -l < "${1:-/dev/stdin}")
-else
-    total_lines=0
-fi
-<<<<<<< HEAD
-
-=======
->>>>>>> 51c97109f287f61e77c97d6ab762010aaff0b428
-# Function to make a call to the local LLM and parse the response
-api_call() {
-    local club_name="$1"
-    local end_of_spell="$2"
-    local temp_output="temp_response.txt" # Temporary file to store LLM response
-
-    # Replace placeholders in the prompt template with local variables
-    local prompt=$(echo "$prompt_template" | sed "s/<club_name>/${club_name}/g; s/<end_of_spell>/${end_of_spell}/g")
-
-    # Call the local LLM model
-    echo "$prompt" | ollama run llama3 > "$temp_output"
-    local response=$(cat "$temp_output")
-
-    # Extract the JSON part from the response
-#   local json_response=$(echo "$response" | sed -n '/<|start_header_id|>assistant<|end_header_id|>/,/<|eot_id|>/p' | sed 's/<|start_header_id|>assistant<|end_header_id|>//' | sed 's/<|eot_id|>//')
-
-    # Increment counter
-    ((counter++))
-    echo "Processing club ${club_name} (${end_of_spell}) - ${counter} of ${total_lines} processed"
-    echo "$prompt"
-    # Write the JSON response to the master output file
-#    echo "$json_response" >> master_output.jsonl
-     echo "$response" >> master_output_test.jsonl
-}
-
-# Read input from a file or stdin
-while IFS= read -r line || [[ -n "$line" ]]; do
-    # Skip the first line (header)
-    [[ "$line" =~ ^club_name,end_of_spell$ ]] && continue
-
-    # Parse the input line to extract club_name and end_of_spell
-    club_name=$(echo "$line" | cut -d ',' -f 1)
[…]

### 2024-06-07 LLM-work/extract_json.py

@@ -1,36 +1,0 @@
-import json
-
-with open("./LLM-work/responses.txt", 'r') as file:
-  file_content = file.read()
-
-# Find the first and last occurrences of '{' and '}'
-start_index = file_content.find('{')
-end_index = file_content.rfind('}')
-
-# Extract the text between the first '{' and the last '}'
-extracted_text = file_content[start_index:end_index + 1]
-
-# Split the extracted text by newline character
-json_strings = extracted_text.split('\n')
-
-# Remove empty strings
-json_strings = [js for js in json_strings if js.strip()]
-
-# Load the JSON strings into a list of dictionaries
-data = []
-for js in json_strings:
-  try:
-    data.append(json.loads(js))
-  except json.JSONDecodeError as e:
-    print(f"Error decoding JSON string: {js}, Error: {e}")
-
-import pandas as pd
-
-# Create a dataframe from the list of dictionaries
-df = pd.DataFrame(data)
-
-# Display the first 5 rows
-print(df.head().to_markdown(index=False, numalign="left", stralign="left"))
-
-# Print the column names and their data types
-print(df.info())

### 2024-06-07 LLM-work/json_objs_extract.py

@@ -1,15 +1,0 @@
-import json
-
-# Open the input and output files
-with open('master_output.jsonl', 'r') as infile, open('output.jsonl', 'w') as outfile:
-    json_object = ''
-    for line in infile:
-        json_object += line.strip()
-        if line.strip().endswith('}'):
-            # Parse the JSON object and re-serialize it into a single-line format
-            data = json.loads(json_object)
-            json_singleline = json.dumps(data, separators=(',', ':'))
-            # Write the single-line JSON object to the output file
-            outfile.write(json_singleline + '\n')
-            # Reset the JSON object
-            json_object = ''

### 2024-06-07 LLM-work/post_process.sh

@@ -1,43 +1,0 @@
-#!/bin/bash
-
-# Post-processing script
-# This script takes the master_output.jsonl file as input
-# and generates a cleaned master_output_cleaned.jsonl file
-# containing only the JSON part of the responses.
-# It also converts the cleaned JSON data to a CSV file.
-
-# Check if the input file is provided
-if [ -z "$1" ]; then
-    echo "Usage: $0 <master_output.jsonl>"
-    exit 1
-fi
-
-input_file="$1"
-cleaned_jsonl_file="master_output_cleaned.jsonl"
-json_file="master_output.json"
-csv_file="master_output.csv"
-
-# Clear the output files
-> "$cleaned_jsonl_file"
-> "$json_file"
-> "$csv_file"
-
-# Process each line of the input file
-while IFS= read -r line; do
-    # Extract the JSON part from the line
-    json_part=$(echo "$line" | sed -n '/^{/,/^}$/p' | jq -c '.')
-
-    # Write the JSON part to the cleaned output file
-    echo "$json_part" >> "$cleaned_jsonl_file"
-done < "$input_file"
-
-# Create a valid JSON array from the cleaned JSONL file
-jq --slurp '.' "$cleaned_jsonl_file" > "$json_file"
-
-# Convert JSON to CSV
-jq -r '[["club_name", "end_of_spell", "spell_type", "country", "tier", "country_probability", "tier_probability"]] + (.[].response.variables[] | [.value, .value]) + (.[].response.results[] | [.value, .value, .value, .value, .value])' "$json_file" > "$csv_file"
-
-echo "Post-processing completed."
-echo "Cleaned output written to $cleaned_jsonl_file"
-echo "JSON output written to $json_file"
-echo "CSV output written to $csv_file"

### 2024-06-07 LLM-work/postprocessing_steps.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-
-# use R to clean up csvs
-Rscript csv_hack.r
-# adjust the API responses
-python adjust_text.py
-# extract the LLM answers
-python extract_answers.py

### 2024-06-07 LLM-work/preprocessing.R

@@ -1,74 +1,0 @@
-library(dplyr)
-library(purrr)
-library(stringr)
-spells <- read.csv("raw_data/manager_spells_from_manager_urls.csv")
-
-# Define season_to_date() function here
-season_to_date <- function(season) {
-  if (is.na(season) | length(gsub("/", "", season)) == 0) {
-    return(NA_real_)
-  }
-  
-  parts <- strsplit(season, "/")[[1]]
-  month <- as.numeric(parts[2])
-  if (month < 8) {
-    year <- paste0("20", substr(parts[1], 1, 2))
-  } else {
-    year <- paste0("19", substr(parts[1], 1, 2))
-  }
-  
-  date_str <- paste0("01/08/", year)
-  as.Date(paste(date_str, collapse = "/"), "%d/%m/%Y")
-}
-
-data_helper <- spells |>
-  mutate(row_id=row_number()) |>
-  filter(is.na(Finish)&contract_expiry!="-") |>
-  select(contract_expiry, Finish,row_id)
-data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
-spells |>
-  mutate(row_id=row_number()) |>
-  left_join(data_helper |> select(-Finish), by="row_id") |>
-  mutate(Start = as.Date(Start),
-         Finish = as.Date(Finish)) |>
-  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
-# find duplicates for name,club,Finish
-#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
-# remove duplicates
-spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells
-terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
-                     "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
-                     "1.FC Köln U17","1.FC Köln Yth.",
-                     "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
-                     "Hertha BSC","F. Düsseldorf",
-                     "Velez Mostar","SSV Reutlingen","FV Ravensburg",
[…]

### 2024-06-07 LLM-work/process_json.py

@@ -1,44 +1,0 @@
-import pandas as pd
-import json
-
-def preprocess_data(raw_data):
-    data = []
-    current_entry = ""
-
-    for line in raw_data.splitlines():
-        line = line.strip()
-        if line:
-            # Accumulate lines until we find a closing brace
-            current_entry += line
-            if line.endswith("}"):
-                try:
-                    entry = json.loads(current_entry)
-
-                    # # Standardize date format (assuming DD/MM/YY)
-                    # if "/" in entry['date']:
-                    #     day, month, year = entry['date'].split("/")
-                    #     entry['date'] = f"20{year}-{month}-{day}"
-
-                    data.append(entry)
-                except json.JSONDecodeError as e:
-                    print(f"Warning: Skipping invalid JSON object: {current_entry} - Error: {e}")
-                finally:
-                    current_entry = ""  # Reset for the next entry
-
-    df = pd.DataFrame(data)
-    return df
-
-# Raw data from the JSON file named master_output.jsonl
-with open("master_output.jsonl") as f:
-    raw_data = f.read()
-
-# Preprocess the data
-df = preprocess_data(raw_data)
-
-# Reorder columns
-df = df[['club', 'date', 'country', 'League', 'Tier']]
-
-# Write to CSV
-df.to_csv("cleaned_football_data.csv", index=False)
-
-print(f"Processed {len(df)} entries and saved to cleaned_football_data.csv")
